\documentclass[12pt, a4paper]{article}

\setcounter{tocdepth}{4}
\setcounter{secnumdepth}{4}

\usepackage[hyphens]{url}
\usepackage[urlcolor=blue]{hyperref}
%\usepackage[disable]{todonotes}
\usepackage[colorinlistoftodos,prependcaption]{todonotes}
\usepackage{amsmath}%
\usepackage{amsfonts}%
\usepackage{amssymb}%
\usepackage{graphicx}
%\usepackage[miktex]{gnuplottex}
%\ShellEscapetrue
\usepackage{epstopdf}
\usepackage{longtable}
\usepackage{floatrow}
\usepackage{minted}
\usepackage{textcomp}
\usepackage{color,soul}
\usepackage[font={small,it}]{caption}
\floatsetup[listing]{style=Plaintop}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true, %set true if you want colored links
    linktoc=all,     %set to all if you want both sections and subsections linked
    linkcolor=blue,  %choose some color if you want links to stand out
}

% Turn off indentation but allow \indent command to still work.
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}

\addtolength{\textwidth}{0.8in}
\addtolength{\oddsidemargin}{-.4in}
\addtolength{\evensidemargin}{-.4in}
\addtolength{\textheight}{1.6in}
\addtolength{\topmargin}{-.8in}

\usepackage{longtable,supertabular}
\usepackage{listings}
\lstset{
  frame=top,frame=bottom,
  basicstyle=\ttfamily,
  language=XML,
  tabsize=2,
  belowskip=2\medskipamount
}

\usepackage{tabu}
\tabulinesep=1.0mm
\restylefloat{table}

\usepackage{siunitx}

\renewcommand\P{\ensuremath{\mathbb{P}}}
\newcommand\E{\ensuremath{\mathbb{E}}}
\newcommand\Q{\ensuremath{\mathbb{Q}}}
\newcommand\I{\mathds{1}}
\newcommand\F{\ensuremath{\mathcal F}}
\newcommand\V{\ensuremath{\mathbb{V}}}
\newcommand\YOY{{\rm YOY}}
\newcommand\Prob{\ensuremath{\mathbb{P}}}
\newcommand{\D}[1]{\mbox{d}#1}
\newcommand{\VR}{\mathit{VR}}
\newcommand{\NPV}{\mathit{NPV}}
\newcommand{\CMS}{\mathit{CMS}}
\newcommand{\CDS}{\mathit{CDS}}
\newcommand{\CVA}{\mathit{CVA}}
\newcommand{\DVA}{\mathit{DVA}}
\newcommand{\FVA}{\mathit{FVA}}
\newcommand{\COLVA}{\mathit{COLVA}}
\newcommand{\FCA}{\mathit{FCA}}
\newcommand{\FBA}{\mathit{FBA}}
\newcommand{\KVA}{\mathit{KVA}}
\newcommand{\MVA}{\mathit{MVA}}
\newcommand{\PFE}{\mathit{PFE}}
\newcommand{\EE}{\mathit{EE}}
\newcommand{\EPE}{\mathit{EPE}}
\newcommand{\ENE}{\mathit{ENE}}
\newcommand{\PD}{\mathit{PD}}
\newcommand{\LGD}{\mathit{LGD}}
\newcommand{\DIM}{\mathit{DIM}}
\newcommand{\IM}{\mathit{IM}}
\newcommand{\bs}{\textbackslash}
\newcommand{\REDY}{\color{red}Y}
\newcommand{\flt}{\mathit{flt}}
\newcommand{\fix}{\mathit{fix}}
\newcommand{\form}{\mathit{form}}
\newcommand{\OIS}{\mathit{OIS}}
\newcommand{\ON}{\mathit{ON}}

\begin{document}

\title{ORE+ Scripted Trade Library - Plausibility Analysis}
\author{Quaternion Risk Management}
\date{28 November 2019}
\maketitle

\newpage

%-------------------------------------------------------------------------------
\section*{Document History}

\begin{supertabular}{|l|l|l|p{7cm}|}
\hline
Version & Date & Author & Comment \\
\hline
0.1 & 28 November 2019 & Niall O'Sullivan & Initial placeholder \\
\hline
\end{supertabular}


\vspace*{\fill}

\textcircled{c} 2019 Quaternion Risk Management Limited.  All rights reserved.
Quaternion\textsuperscript{\textregistered} is a trademark of Quaternion Risk Management Limited and is also registered
at the UK Intellectual Property Office and the U.S. Patent and Trademark Office.  All other trademarks are the property
of their respective owners. Open Source Risk Engine\textsuperscript{\textcircled{c}} (ORE) is sponsored by Quaternion
Risk Management Limited.

\newpage

\tableofcontents

\newpage

\section{Summary}

This document describes the library of officially supported ORE+ scripts that can be used via the scripted library. Other client and project scripts can be used and these are not covered here. This document contains a list of these scripts, the master location (typically an OpenXVA RegressionTest) and a short section describing the testing and plausibility analysis that was done.

\vspace{3mm}
\noindent
This document is intended for internal Quaternion usage and should not be routinely shared externally.

\subsection{Official Scripts}

The following scripts are supported by ORE+

\begin{itemize}
\item Accumulator
\item WindowBarrier
\item TaRF
\end{itemize}

\section{Scripts}

Each script is described individually here

% Each script gets it's own subsection here detailing it's location and analysis.
\input{accumulator.tex}
\input{windowbarrier.tex}
\input{tarf.tex}
\end{document}
