\subsubsection{Equity Margin Leg}
\label{ss:equitymarginleg}

An equity margin leg is specified in a \lstinline!LegData! node with \lstinline!LegType! set to \lstinline!EquityMargin!. It is used to define a sequence of cashflows that are linked to an equity price and it's associated margin factor. Each cashflow has an associated \textit{Calculation Period}. This leg is typically used to represent a part of a Total Return Swap (TRS) on an Equity Index Future. The full TRS on the Equity Index Future uses TradeType \emph{Swap}, and one leg of type \emph{Equity}, and the other leg of type \emph{EquityMargin}. Note that the equity identifier on both legs (the Name field) should be for the Equity Index, and not the Future. \\
\medskip
The outline of a equity margin leg is given in listing \ref{lst:equitymarginleg}. It has the usual \lstinline!LegData! elements described in section \ref{ss:leg_data} and a \lstinline!EquityMarginLegData! node that is described in section \ref{ss:equity_margin_leg_data} below.

\begin{listing}[h!]
\begin{minted}[fontsize=\footnotesize]{xml}
<LegData>
  <LegType>EquityMargin</LegType>
  <Payer>true</Payer>
  <Currency>EUR</Currency>
  <PaymentConvention>Following</PaymentConvention>
  <PaymentLag>2D</PaymentLag>
  <PaymentCalendar>TARGET</PaymentCalendar>
  <ScheduleData>
       <Dates>
        <Dates>
         <Date>2019-12-31</Date>
         <Date>2020-03-30</Date>
         <Date>2020-06-30</Date>
         <Date>2020-09-30</Date>
         <Date>2020-12-30</Date>
         <Date>2021-03-30</Date>
       </Dates>
     </Dates>
  </ScheduleData>
  <PaymentDates>
    <PaymentDate>...</PaymentDate>
  </PaymentDates>
  <EquityMarginLegData>
    ...
  </EquityMarginLegData>
</LegData>
\end{minted}
\caption{Equity Margin leg outline.}
\label{lst:equitymarginleg}
\end{listing}

\subsubsection{Equity Margin Leg Data}
\label{ss:equity_margin_leg_data}
The \lstinline!EquityMarginLegData! node outline is shown in listing \ref{lst:equitymarginleg}. The meaning and allowable values for each node are as follows:

\begin{itemize}

\item
\lstinline!Rates!: The fixed real rate(s) of the leg. While this can be a single value, a vector of values or a dated vector of
  values. Allowable values: Each rate element can take any  real number. The rate is expressed in decimal form, e.g. \emph{0.05} is a rate of 5\%..

\item
\lstinline!InitialMarginFactor!: this node is used to specify the equity margin factor for the first period of the trade. It's a percentage that reflecting the current applicable official Exchange initial margin requirement. It is expressed in decimal form, e.g. \emph{0.05} is a rate of 5\%..

\item
\lstinline!EquityLegData!: this node is used to specify the underlying equity details. It's values are as outlined in section \ref{ss:equitylegdata}.

\item
\lstinline!Multiplier! [Optional]: in some cases, the cashflow amounts are multiplied by a fixed amount. Defaults to 1.

\end{itemize}

\begin{listing}[h!]
\begin{minted}[fontsize=\footnotesize]{xml}
<EquityMarginLegData>
  <Rates>
    <Rate>0.003</Rate>
  </Rates>
  <InitialMarginFactor>0.12</InitialMarginFactor>
  <Multiplier>10</Multiplier>
  <EquityLegData>
     <ReturnType>Total</ReturnType>
     <Name>RIC:.STOXX50E</Name>
     <InitialPrice>2946</InitialPrice>
     <NotionalReset>false</NotionalReset>
     <FixingDays>2</FixingDays>
  </EquityLegData>
</EquityMarginLegData>
\end{minted}
\caption{Equity margin leg data outline.}
\label{lst:equity_margin_leg_data}
\end{listing}
