\subsubsection{Fixed Leg Data and Rates}
\label{ss:fixedleg_data}

The \lstinline!FixedLegData! trade component node is used within the \lstinline!LegData! trade component when the
\lstinline!LegType! element is set to \emph{Fixed}. The \lstinline!FixedLegData! node only includes the
\lstinline!Rates! sub-node which contains the rates of the fixed leg as child elements of type \lstinline!Rate!.

An example of a \lstinline!FixedLegData! node for a fixed leg with constant notional is shown in Listing \ref{lst:fixedleg_data}.
\begin{listing}[H]
%\hrule\medskip
\begin{minted}[fontsize=\footnotesize]{xml}
              <FixedLegData>
                    <Rates>
                        <Rate>0.05</Rate>
                    </Rates>
              </FixedLegData>
\end{minted}
\caption{Fixed leg data}
\label{lst:fixedleg_data}
\end{listing}

The meanings and allowable values of the elements in the \lstinline!FixedLegData! node follow below.

\begin{itemize}

\item Rates: This node contains child elements of type
  \lstinline!Rate!. If the rate is constant over the life of the fixed
  leg, only one rate value should be entered. If two or more coupons
  have different rates, multiple rate values are required, each
  represented by a \lstinline!Rate! child element. The first rate
  value corresponds to the first coupon, the second rate value
  corresponds to the second coupon, etc. If the number of coupons
  exceeds the number of rate values, the rate will be kept flat at the
  value of last entered rate for the remaining coupons.  The number of
  entered rate values cannot exceed the number of coupons. 

  Allowable values: Each child element can take any  real number. The rate is
  expressed in decimal form, e.g. 0.05 is a rate of 5\%.

As in the case of notionals, the rate schedule can be specified with
dates as shown in Listing \ref{lst:fixedleg_data_dates}.
\begin{listing}[H]
%\hrule\medskip
\begin{minted}[fontsize=\footnotesize]{xml}
              <FixedLegData>
                    <Rates>
                        <Rate>0.05</Rate>
                        <Rate startDate='2016-02-04'>0.05</Rate>
                        <Rate startDate='2019-02-05'>0.05</Rate>
                    </Rates>
              </FixedLegData>
\end{minted}
\caption{Fixed leg data with 'dated' rates}
\label{lst:fixedleg_data_dates}
\end{listing}

\end{itemize}
