\subsubsection{Premiums}
\label{ss:premiums}

The \lstinline!Premiums! node holds data of one or more premiums to be paid. It is used in different trade types,
notably in caps / floors (see section \ref{ss:capfloor}) and more generally in the option data component (see section
\ref{ss:option_data}). Listing \ref{lst:premiums} shows an example for a Premiums data block representing two premiums.

\begin{listing}[H]
%\hrule\medskip
\begin{minted}[fontsize=\footnotesize]{xml}
<Premiums>
  <Premium>
    <Amount>1000</Amount>
    <Currency>EUR</Currency>
    <PayDate>2021-01-27</PayDate>
    <SettlementData>...</SettlementData>
  </Premium>
  <Premium>
    <Amount>5000</Amount>
    <Currency>USD</Currency>
    <PayDate>2023-01-27</PayDate>
  </Premium>
</Premiums>
\end{minted}
\caption{Premiums Node}
\label{lst:premiums}
\end{listing}

The meanings and allowable values of the elements in the \lstinline!Premium! node follow below.

\begin{itemize}
\item Amount: Option premium amounts paid by the option buyer to the option seller. A positive amount is considered to be paid by the option holder to the option seller and thus results in a negative contribution to the NPV of a long option. \\
  Allowable values: arbitrary number
\item Currency: Currency of the premium to be paid\\
  Allowable values:  See Table \ref{tab:currency} \lstinline!Currency!.
\item PayDate: Date of the premium payment.\\
  Allowable values:  See \lstinline!Date! in Table \ref{tab:allow_stand_data}.
\item SettlementData [Optional]: Converts the premium into a currency different. It specifies the payment currency, the FX index to perform the conversion, and the date on which the FX rate is fixed. Its XML form is shown in listing \ref{lst:settlement_data_premiums}.
\begin{itemize}
  \item \lstinline!PayCurrency!: Currency in which the option premium will be settled.
  \item \lstinline!FXIndex!: FX index used to convert from the premium currency into the settlement currency.
  \item \lstinline!FixingDate!: Date on which the FX rate is taken. If omitted, the engine will use the index convention to derive the fixing date from the payment date.
\end{itemize}
\end{itemize}

We support a deprecated schema to represent a single premium as shown in listing \ref{lst:premiums_deprecated} for
backwards compatibility. The $3$ nodes PremiumAmount, PremiumCurrency, PremiumPayDate can be used on the same level as
the new Premiums node to represent a single premium payment. The deprecated and new schema may not be mixed.

\begin{listing}[H]
%\hrule\medskip
\begin{minted}[fontsize=\footnotesize]{xml}
  <PremiumAmount>1000</PremiumAmount>
  <PremiumCurrency>EUR</PremiumCurrency>
  <PremiumPayDate>2021-01-27</PremiumPayDate>
\end{minted}
\caption{Deprecated Single Premium Representation}
\label{lst:premiums_deprecated}
\end{listing}


\begin{listing}[H]
\begin{minted}[fontsize=\footnotesize]{xml}
<SettlementData>
  <PayCurrency>USD</PayCurrency>
  <FXIndex>FX-ECB-EUR-USD</FXIndex>
  <FixingDate>2020-03-28</FixingDate>
</SettlementData>
\end{minted}
\caption{SettlementData node for option premiums}
\label{lst:settlement_data_premiums}
\end{listing}
