\subsubsection{RangeBound}
\label{ss:rangebound}
This trade component node is used within the following trade data containers

\begin{itemize}
  \item FxTaRFfData, EquityTaRFData, CommodityTaRFData
  \item FxAccumulatorData, EquityAccumulatorData, CommodityAccumulatorData
\end{itemize}

An example structure of the \lstinline!RangeBound! trade component node is shown in Listing
\ref{lst:rangebound}.

\begin{listing}[H]
%\hrule\medskip
\begin{minted}[fontsize=\footnotesize]{xml}
        <RangeBound>
          <RangeFrom>0</RangeFrom>
          <RangeTo>155.00</RangeTo>
          <Leverage>2</Leverage>
          <Strike>150.54</Strike>
        </RangeBound>
\end{minted}
\caption{RangeBound}
\label{lst:rangebound}
\end{listing}

The meanings and allowable values of the elements in the \lstinline!RangeBound! node follow below.

\begin{itemize}
\item RangeFrom [Optional]: The lower bound of the range. 

Allowable values:  Any real number. If omitted, no lower bound applies. Cannot be left blank.

\item RangeTo [Optional]: The upper bound of the range. 

Allowable values:  Any real number. If omitted, no lower bound applies. Cannot be left blank.

\item Leverage [Optional]: The leverage that applies to the range. For TaRFs, negative leverage can be mixed with positive leverage to reflect a TaRF with switching buyer/seller. However, for Accumulators all given Leverage parameters within the same instrument (in multiple \lstinline!RangeBound! nodes) must have the same sign.

Allowable values:  Any real number. Defaults to 1 if omitted. Cannot be left blank.

\item Strike [Optional]: The strike specific to the range. If given overwrites a strike given on the trade level.

Allowable values:  Any real number. Defaults to the trade level strike if omitted. Cannot be left blank.

\item StrikeAdjustment [Optional]: A strike adjustment relative to the strike given on the trade level.  If given the
  strike for the defined range is computed as $K+A$ where $K$ is the strike on the trade level and $A$ is the strike
  adjustment. Notice that Strike and StrikeAdjustment can not be given both at the same time.

Allowable values:  Any real number.
\end{itemize}
