%========================================================
\section{Collateral Balances}\label{sec:collateralbalances}
%========================================================

The collateral balances file - {\tt collateralbalances.xml} - 
contains the list of collateral balances (i.e.\ margin amounts
and independent amount) under a Credit Support Annex.

\vspace{1em}

The balances of each netting set are defined within their own
\lstinline!CollateralBalance! node. All of these
\lstinline!CollateralBalance! nodes are contained as children
of a \lstinline!CollateralBalances! node.

\vspace{1em}

The collateral balances are given in the following XML template:

\begin{listing}[H]
%\hrule\medskip
\begin{minted}[fontsize=\footnotesize]{xml}
    <CollateralBalances>
        <CollateralBalance>
            <NettingSetId> </NettingSetId>
            <Currency>USD</Currency>
            <IndependentAmountHeld/>
            <InitialMargin> </InitialMargin>
            <VariationMargin> </VariationMargin>
        </CollateralBalance>
        <CollateralBalance>
            .......
        </CollateralBalance>
    </CollateralBalances>
\end{minted}
\caption{Collateral balance definition}
\label{lst:collateralbalances}
\end{listing}

The meanings of the various elements of the \lstinline!CollateralBalance!
node are as follows (default input values for certain analytics are
specified in their own respective sections, otherwise the
defaults given below, if any, are applicable):
\begin{itemize}
\item \lstinline!NettingSetId!: The unique identifier for the (collateralised) ISDA netting set.
\ifdefined\RiskCatalogue{ Alternatively, a \lstinline!NettingSetDetails! node can be used, see Section
\ref{sec:nettingsetdetails}.}\fi \\
  Allowable values: Any string.
\item \lstinline!Currency!: The currency that the collateral balance amounts are assumed to be
denominated in.\\
  Allowable values: See Table \ref{tab:currency}.
\item \lstinline!IndependentAmountHeld! [Optional]: The netted sum of all independent amounts
covered by the CSA.\\
  Allowable values: Any number. A negative number implies that the counterparty holds
  the independent amount. If provided, overrides the specified independent amount held (if any)
  in the corresponding netting set definitions file. Otherwise (if left blank or omitted),
  the independent amount in the netting set definitions file is used.
\item \lstinline!InitialMargin! [Optional]: The initial margin amount received.\\
  Allowable values: Any number. A negative number implies that the counterparty holds
  the initial margin.
\item \lstinline!VariationMargin! [Optional]: The variation margin amount received.\\
  Allowable values: Any number. A negative number implies that the counterparty holds
  the variation margin.
\end{itemize}
