The payoffs described in the Trade Specific Data for scripted trades usually involve a payment currency.
Unless stated otherwise, this currency represents the {\em natural} payoff currency, i.e.

\begin{itemize}
\item for equity and commodity underlyings this should be the currency in which the underlying price is quoted
\item for FX underlyings \lstinline!FX-SOURCE-CCY1-CCY2! this should be the domestic (target, numeraire) currency \lstinline!CCY2!.
\end{itemize}

If the payment currency is set to a different currency on the other hand, the resulting payoff is a true quanto payoff,
i.e.\ the amount of the payoff is determined on the natural currency, but paid in a different currency {\em without}
converting the amount to this latter currency using the fair FX Spot rate on the settlement date.

We are aware that a conversion from the natural payoff currency to a different settlement currency using the fair FX
Spot rate is sometimes part of the terms and conditions of a trade. This conversion has no or small impact on the
valuation and risk profile of a trade though and is therefore usually not part of the payoff modeling.

As an example consider a Forward Volatility Agreement on the FX pair GBP-EUR. The \lstinline!PayCcy! should be set to EUR in this
case, even if the forward premium is settled in GBP as it is usual market practice for this pair.

Notice that the above does not apply to fixed premiums, where the premium is given as a fixed number in the trade xml
together with a premium currency in which this amount should be paid.