\subsubsection{Equity Option}

The \lstinline!EquityOptionData!  node is the trade data container for the equity option trade type.  Vanilla equity 
options are supported, the exercise style must be \emph{European}. The \lstinline!EquityOptionData!  node includes one and 
only one \lstinline!OptionData! trade component sub-node plus elements specific to the equity option. The structure of 
an example \lstinline!EquityOptionData! node for an equity option is shown in Listing
\ref{lst:eqoption_data}.

\begin{listing}[H]
%\hrule\medskip
\begin{minted}[fontsize=\footnotesize]{xml}
<EquityOptionData>
    <OptionData>
      ...
    </OptionData>
    <Name>ISIN:US78378X1072</Name>
    <Currency>USD</Currency>
    <Strike>2147.56</Strike>
    <Quantity>17000</Quantity>
</EquityOptionData>
\end{minted}
\caption{Equity Option data}
\label{lst:eqoption_data}
\end{listing}

The meanings and allowable values of the elements in the \lstinline!EquityOptionData!  node follow below.

\begin{itemize}
	\item OptionData: This is a trade component sub-node outlined in section \ref{ss:option_data} Option Data. Note 
	that the equity option type allows for \emph{European} option style only.	
	\item Name: The ISIN of the underlying equity or equity index. \\
	Allowable values:  ISINs for supported equity indices and single names. See Equity Name in Table \ref{tab:equityname}.	
	\item Currency: The currency of the equity option. \\
	Allowable values:  See \lstinline!Currency!  in Table \ref{tab:allow_stand_data}.	
	\item Strike: The option strike price.\\
	Allowable values:  Any positive real number.	
	\item Quantity: The number of units of the underlying covered by the transaction. \\
	Allowable values:  Any positive real number.
\end{itemize}