\subsubsection{Equity Forward}

The \lstinline!EquityForwardData!  node is the trade data container for the equity forward trade type.  Vanilla equity 
forwards are supported. The structure of an example \lstinline!EquityForwardData! node for an equity option is shown in 
Listing \ref{lst:eqfwd_data}.

\begin{listing}[H]
%\hrule\medskip
\begin{minted}[fontsize=\footnotesize]{xml}
<EquityForwardData>
  <LongShort>Long</LongShort>
  <Maturity>2018-06-30</Maturity>
  <Name>ISIN:US78378X1072</Name>
  <Currency>USD</Currency>
  <Strike>2147.56</Strike>
  <Quantity>17000</Quantity>
</EquityForwardData>
\end{minted}
\caption{Equity Forward data}
\label{lst:eqfwd_data}
\end{listing}

The meanings and allowable values of the elements in the \lstinline!EquityForwardData!  node follow below.

\begin{itemize}
	\item LongShort: Defines whether the underlying equity will be bought (long) or sold (short). \\
	Allowable values: \emph{Long}, \emph{Short}.
	\item Maturity: The maturity date of the forward contract, i.e. the date when the underlying equity will be bought/sold. \\
	Allowable values: Any date string, see \lstinline!Date! in Table \ref{tab:allow_stand_data}.
	\item Name: The ISIN of the underlying equity or equity index. \\
	Allowable values:  The prefix {\tt ISIN:} followed by an ISIN code for supported equity indices and single names. See Equity Name in Table \ref{tab:equityname}.	
	\item Currency: The  currency of the equity forward. \\
	Allowable values:  See  \lstinline!Currency! in Table \ref{tab:allow_stand_data}.	
	\item Strike: The agreed buy/sell price of the equity forward. \\
	Allowable values:  Any positive real number.	
	\item Quantity: The number of units of the underlying equity to be bought/sold. \\
	Allowable values:  Any positive real number.
\end{itemize}