\subsubsection{Cap/Floor}
\label{ss:capfloor}

\ifdefined\IncludePayoff{{\bf Payoff}

A single floating swap leg with interest payments benchmarked to IBOR or CMS 
indices, may have a cap, floor, or collar. This creates a series of European 
interest rate options (caplets or floorlets) where the cap or floor rate is the 
strike price, and each floating rate reset date is an option expiry date. \\

A collar is the combination of a series of long caplets and short floorlets 
for a long position in the collar. \\

Payoff of a caplet on an IBOR floating leg coupon period to the payer of the 
leg (the option buyer):
$$
N[L(t_{i-1},t_i)-K]^+ \delta(t_{i-1}, t_i) 
= N \,\max(0,L(t_{i-1},t_i)-K)\,\delta(t_{i-1}, t_i)
$$

Payoff of a floorlet on an IBOR floating leg coupon period to the receiver of 
the leg (the option buyer):
$$
N[K-L(t_{i-1},t_i)]^+ \delta(t_{i-1}, t_i)
= N \,\max(0,K-L(t_{i-1},t_i)) \,\delta(t_{i-1}, t_i)
$$

Where:
\begin{itemize}
\item $N$: the Notional
\item $L(t_{i-1},t_i)$: the IBOR index fixing for the period
\item $K$: the cap or floor rate, i.e. the strike
\item $\delta(t_{i-1},t_i)$: the daycount fraction for the coupon period 
\end{itemize}

For a caplet or floorlet on a CMS index the $L(t_{i-1},t_i)$ index can be 
replaced by $\CMS_n$ where $n$ indicates CMS rate for $n$ number of years.
	
Standalone caps and floors with a single payoff on an IBOR or CMS index are 
also supported. Payoff of a cap/floor on an IBOR index:
$$
N\cdot \left[\omega(L(t_{i-1},t_i)-K)\right]^+
$$
where $\omega=1$ for a cap, $\omega=-1$ for a floor.\\

Payoff of a cap/floor on a CMS index:
$$
N \cdot \left[\omega(\CMS_n - K)\right]^+
$$
where $\CMS_n$ is the n year CMS rate.

{\bf Input}}\fi


The \lstinline!CapFloorData! node is the trade data container for the \emph{CapFloor} trade type.  It's a cap, floor or
collar (i.e. a portfolio of a long cap and a short floor for a long position in the collar) on a series of Ibor, SIFMA,
OIS, CMS, Duration-adjusted CMS, CMS Spread, CPI, YY coupons.

The \lstinline!CapFloorData! node contains a \lstinline!LongShort! sub-node which indicates whether the cap (floor, collar)
is long or short, and a \lstinline!LegData!  sub-node where the
LegType can be set to \emph{Floating}, \emph{CMS}, \emph{CMSSpread}, \emph{DurationAdjustedCMS}, \emph{CPI}
or \emph{YY}, plus elements for the Cap and Floor rates. An example structure with Cap rates is shown in in Listing
\ref{lst:capfloor_data}. The optional node \emph{PaymentDates} in the \lstinline!LegData! subnode is currently only used for OIS and IBOR indices (see \ref{ss:leg_data}).

A \lstinline!CapFloorData! node must have either \lstinline!Caps! or \lstinline!Floors!
elements, or both. In the case of both (I.e. a collar with long cap and short floor) the sequence is that  \lstinline!Caps! elements must be above the \lstinline!Floors! elements. Note that 
the \lstinline!Caps! and \lstinline!Floors! elements must be outside the \lstinline!LegData! sub-node, i.e. a \emph{CapFloor} 
can't have a capped or floored  \emph{Floating}  or \emph{CMS} leg.
The \emph{Payer} flag in the LegData subnode is ignored for this instrument. Notice that the signs in the definition of a collar (long cap, short floor) for the CapFloor
instruments is exactly opposite to \ref{ss:floatingleg_data}.

\begin{listing}[H]
%\hrule\medskip
\begin{minted}[fontsize=\footnotesize]{xml}
<CapFloorData>
  <LongShort>Long</LongShort>
  <LegData>
    <Payer>false</Payer>
    <LegType>Floating</LegType>
     ...
  </LegData>
  <Caps>
    <Cap>0.05</Cap>
  </Caps>
  <Premiums>
    <Premium>
      <Amount>1000</Amount>
      <Currency>EUR</Currency>
      <PayDate>2021-01-27</PayDate>
    </Premium>
  </Premiums>
</CapFloorData>
\end{minted}
\caption{Cap/Floor data}
\label{lst:capfloor_data}
\end{listing}

The meanings and allowable values of the elements in the \lstinline!CapFloorData!  node follow below.

\begin{itemize}

\item LongShort: This node defines the position in the cap (floor, collar) and can take values \emph{Long} or \emph{Short}.

\item LegData: This is a trade component sub-node outlined in section \ref{ss:leg_data}. Exactly
  one \lstinline!LegData! node is allowed, and the LegType element must
  be set to \emph{Floating} (Ibor and OIS), \emph{CMS}, \emph{CMSSpread}, \emph{DurationAdjustedCMS}, \emph{CPI} or \emph{YY}.

\item Caps: This node has child elements of type \lstinline!Cap!
  capping the floating leg (after applying spread if any). The first rate value corresponds to the
  first coupon, the second rate value corresponds to the second
  coupon, etc. If the number of coupons exceeds the number of rate
  values, the rate will be kept flat at the value of last entered rate
  for the remaining coupons. For a fixed cap rate over all coupons,
  one single rate value is sufficient. The number of entered rate
  values cannot exceed the number of coupons.  

  Allowable values for each \lstinline!Cap! element: Any real number. The rate is expressed in decimal form, eg 0.05 is
  a rate of 5\%

\item Floors: This node has child elements of type
  \lstinline!Floor! flooring the floating leg (after applying spread if any).  The first rate value
  corresponds to the first coupon, the second rate value corresponds
  to the second coupon, etc. If the number of coupons exceeds the
  number of rate values, the rate will be kept flat at the value of
  last entered rate for the remaining coupons. For a fixed floor rate
  over all coupons, one single rate value is sufficient. The number of
  entered rate values cannot exceed the number of coupons.

  Allowable values for each \lstinline!Floor! element: Any real number. The rate is expressed in decimal form, eg 0.05 is
  a rate of 5\%

\item Premiums [Optional]: Option premium amounts paid by the option buyer to the option seller.

Allowable values:  See section \ref{ss:premiums}

\end{itemize}
