\subsubsection{CPI Swap}

\ifdefined\IncludePayoff{{\bf Payoff}

A CPI swap is an inflation swap where one of the legs has a floating rate with 
coupon payments linked to a supported inflation index.  

Coupons on the inflation leg are calculated starting by the contractual real 
coupon rate and adjusting it to a nominal rate using the change from the relevant 
inflation index fixing before issue date to the index fixing at coupon reset date, 
taking into account observation lag, and if necessary, interpolation between 
inflation index fixings.

Note that the amount to be disbursed on the maturity date of the inflation leg 
(excluding the last coupon) is calculated by multiplying the initial notional 
(face value) value by the increase in the relevant inflation index over the life 
of the swap. A CPI Swap coupon payment at time i:
$$
N\,r\,\frac{I(T_i)}{I(T_0)}\,\delta(T_{i-1}, T_i)
$$
where:
\begin{itemize}
\item $N$: notional
\item $r$: the contractual real rate
\item $I(T_i)$: the relevant CPI fixing for time $T_i$
\item $I(T_0)$: the relevant CPI fixing before issue date
\item $\delta(T_{i-1}, T_i)$: the day count fraction for the accrual period up to 
time $T_i$
\end{itemize}

The flow at maturity excluding the last coupons can be either no flow on both legs, 
or the notional on the non-inflation leg and the following on the inflation leg:
$$
N\,\frac{I(T)}{I(T_0)}
$$
where $I(T)$ is the relevant CPI fixing for the maturity date.

\medskip
CPI linked coupons and maturity cashflows can be capped/floored. 

{\bf Input}}\fi

A CPI inflation swap can be set up using the \emph{InflationSwap} trade type, with one leg of type {\tt CPI}. and the other leg(s) can be of any leg type. Listing \ref{lst:cpiinflationswap} shows an example. The CPI leg contains an additional {\tt CPILegData} block. See \ref{ss:cpilegdata} for details on the
CPI leg specification. 

Note that Cross Currency Inflation Swaps are supported, as the currencies on the legs of an  \emph{InflationSwap} do not need to be the same. 


\begin{listing}[H]
%\hrule\medskip
\begin{minted}[fontsize=\footnotesize]{xml}
    <InflationSwapData>
      <LegData>
        <LegType>Floating</LegType>
        <Payer>true</Payer>
        ...
      </LegData>
      <LegData>
        <LegType>CPI</LegType>
        <Payer>false</Payer>
        ...
        <CPILegData>
        ...
        </CPILegData>
      </LegData>
    </InflationSwapData>
\end{minted}
\caption{CPI Swap Data (using \emph{InflationSwap} trade type)}
\label{lst:cpiinflationswap}
\end{listing}


Alternatively, a CPI swap can be set up as a swap with trade type \emph{Swap}, with one leg of type {\tt CPI}, see listing \ref{lst:cpiswap}.

\begin{listing}[H]
%\hrule\medskip
\begin{minted}[fontsize=\footnotesize]{xml}
    <SwapData>
      <LegData>
        <LegType>Floating</LegType>
        <Payer>true</Payer>
        ...
      </LegData>
      <LegData>
        <LegType>CPI</LegType>
        <Payer>false</Payer>
        ...
        <CPILegData>
        ...
        </CPILegData>
      </LegData>
    </SwapData>
\end{minted}
\caption{CPI Swap Data (using \emph{Swap} trade type)}
\label{lst:cpiswap}
\end{listing}

