\subsubsection{Credit Linked Swap}

\ifdefined\IncludePayoff{{\bf Payoff}

A credit linked swap is a swap where the payments are contingent on credit events occuring for a reference CDS. There
are three classes of payments.

\begin{itemize}
\item Payments that are made only if no credit event has occured for a reference CDS until the payment date. If a credit
  event occurs within a coupon period the accrued amount until the credit event date might have to be paid or not,
  dependent on the terms of the trade. The accrual payment is done on the credit event date (with a small settlement
  delay in practice).
\item Payments that are made in case a credit {\em has} occured, the amount is then weighted by either
  \begin{itemize}
  \item the actual recovery rate $RR$ associated to the credit event or
  \item the loss given default rate $1-RR$ based on the actual recovery rate or
  \item a fixed (digital) recovery rate $RR$, agreed upon in the trade terms or
  \item a fixed loss given default rate $1-RR$
  \end{itemize}
  These payments can be agreed to be made on the default date (with a small settlement delay in practice), on the period
  end date for the respective payment or on the trade maturity.
\item Payments that are made independently of any credit events occuring for the reference CDS.
\end{itemize}

The underlying swap legs can pay any kind of coupon (fixed rate, Ibor, CMS, ...) or fixed amounts.

{\bf Input}}\fi

A credit linked swap, trade type \lstinline!CreditLinkedSwap!, is set up using a \lstinline!CreditLinkedSwapData! block
as shown in listing \ref{lst:creditlinkedswap}. The elements have the following meaning:

\begin{itemize}
\item CreditCurveId: The referenced CDS credit curve. \\
  Allowable values: See \lstinline!CreditCurveId! for credit trades - single name in Table
  \ref{tab:equity_credit_data}. A \lstinline!ReferenceInformation! node may be used in place of this
  \lstinline!CreditCurveId! node.
\item SettlesAccrual [Optional]: A flag indicating whether accrued coupon amounts are paid in case of a credit
  event. Optional, defaults to \verb+true+. Applies to the payments specified under ContingentPayments.\\
  Allowable values: true, false
\item FixedRecoveryRate [Optional]: A fixed (digital) recovery rate to apply. If not given, the market recovery rate
  is used. Applies to the payments specified under DefaultPayments and RecoveryPayments.\\
  Allowable values: Any non-negative real number.
\item DefaultPaymentTime [Optional]: Controls the timing of the payments specified under DefaultPayments and
  RecoveryPayments. Defaults to \lstinline!atDefault!. \\
  Allowable values: \lstinline!atDefault!, \lstinline!atPeriodEnd!, \lstinline!atMaturity!.
\item IndependentPayments [Optional]: The legs for which payments are made independent from credit events. The node contains one or
  more \lstinline!LegData! subnodes representing these legs. Optional, can be omitted if no such payments are made. \\
  Allowable values: See \ref{ss:leg_data} for the \lstinline!LegData! subnode structure.
\item ContingentPayments [Optional]: The legs for which payments are contingent on no credit event having occured until
  the payment date. If no such payments are made, the node can be omitted. \\
  Allowable values: See \ref{ss:leg_data} for the \lstinline!LegData! subnode structure.
\item DefaultPayments [Optional]: The legs for which payments are contingent on a credit event having occured. If no
  such payments are made, the node can be omitted. If a default happens at a date d, the associated payment is the
  earliest payment with date greater or equal to d. \\
  Allowable values: See \ref{ss:leg_data} for the \lstinline!LegData! subnode structure.
\item RecoveryPayments [Optiopnal]: The legs for which payments are contingent on a credit event having occured. The
  node works analogously to the DefaultPayments node, the only difference is that that payment amounts are weighted by
  $RR$ instead of $1-RR$. \\
  Allowable values: See \ref{ss:leg_data} for the \lstinline!LegData! subnode structure.
\end{itemize}

All legs must be given in the same currency.

\begin{listing}[H]
\begin{minted}[fontsize=\footnotesize]{xml}
  <CreditLinkedSwapData>
    <CreditCurveId>RED:46A844|SNRFOR|USD|XR14</CreditCurveId>
    <SettlesAccrual>false</SettlesAccrual>
    <FixedRecoveryRate>0.4</FixedRecoveryRate>
    <DefaultPaymentTime>atDefault</DefaultPaymentTime>
    <IndependentPayments>
      <LegData> ... </LegData>
      <LegData> ... </LegData>
      ...
    </IndependentPayments>
    <ContingentPayments>
      <LegData> ... </LegData>
      <LegData> ... </LegData>
      ...
    </ContingentPayments>
    <DefaultPayments>
      <LegData> ... </LegData>
      <LegData> ... </LegData>
      ...
    </DefaultPayments>
    <RecoveryPayments>
      <LegData> ... </LegData>
      <LegData> ... </LegData>
      ...
    </RecoveryPayments>
  </CreditLinkedSwapData>
\end{minted}
\caption{Credit Linked Swap Data}
\label{lst:creditlinkedswap}
\end{listing}
