\subsubsection{EQ Accumulator}

EQ Accumulators are represented as scripted trades, refer to appendix A for an introduction. Listing \ref{lst:eqaccumulator} shows the structure of an example.
The \verb+PerformanceOption_01+ node is the trade data container for the PerformanceOption\_01 trade type, listing
\ref{lst:eqaccumulator} shows the structure of an example.

\begin{listing}[H]
\begin{minted}[fontsize=\footnotesize]{xml}
<Trade id="SCRIPTED_EQ_ACCUMULATOR">
  <TradeType>ScriptedTrade</TradeType>
  <Envelope>
    <CounterParty>CPTY_A</CounterParty>
    <NettingSetId>CPTY_A</NettingSetId>
    <AdditionalFields/>
  </Envelope>
  <AccumulatorData>
    <Strike type="number">12.24</Strike>
    <FixingAmount type="number">775</FixingAmount>
    <LongShort type="longShort">Long</LongShort>
    <Underlying type="index">EQ-Lufthansa</Underlying>
    <PayCcy type="currency">EUR</PayCcy>
    <FixingDates type="event">
      <ScheduleData>
        <Dates>
          <Dates>
            <Date>2021-01-29</Date>
          </Dates>
        </Dates>
      </ScheduleData>
      <ApplyCoarsening>true</ApplyCoarsening>
    </FixingDates>
    <RangeUpperBounds type="number">
      <Value>10000</Value>
    </RangeUpperBounds>
    <RangeLowerBounds type="number">
      <Value>0</Value>
    </RangeLowerBounds>
    <RangeLeverages type="number">
      <Value>1</Value>
    </RangeLeverages>
    <KnockOutLevel type="number">1000</KnockOutLevel>
    <GuaranteedFixings type="number">1</GuaranteedFixings> 
  </AccumulatorData>
</Trade>
\end{minted}
\caption{EQ Accumulator Scripted Representation}
\label{lst:eqaccumulator}
\end{listing}

The meanings and allowable values of the elements in the \verb+EQ Accumulator+  representation follow below.

\begin{itemize}
\item Strike: The strike value the equity is purchased at.
\item FixedAmount: The unleveraged quantity accumulated at each fixing date
\item LongShort: 1 for a long, -1 for a short position
\item Underlying: The underlying EQ Index. This must be of the form "EQ-NAME"
\item PayCcy: The payment currency of the trade
\item FixingDates: The fixing dates, given as a ScheduleData node
\item RangeUpperBound: Values of upperbounds for the leverage ranges. If a given range has no upperbound add 100000
\item RangeLowerBound: Values of lowerbounds for the leverage ranges. If a given range has no lowerbound add 0
\item RangeLeverages: Values of leverages for the leverage ranges.
\item KnockOutLevel: The KnockOut Barrier level
\item GuaranteedFixings: Number of the first n Fixings that are guaranteed, regardless of whether or not the trade has been knocked out.
\end{itemize}

The script `Accumulator' referenced in the trade above is shown in Listing \ref{lst:accumulator_script}.

\begin{listing}[H]
\begin{minted}[fontsize=\footnotesize]{xml}

NUMBER Payoff, fix, d, r, Triggered;
Payoff = 0;
Triggered = -1;
FOR d IN (1, SIZE(FixingDates)) DO
    fix = Underlying(FixingDates[d]);
    
    IF fix >= KnockOutLevel THEN
      Triggered = 1;
    END;
    IF Triggered != 1 OR d <= GuaranteedFixings THEN
        FOR r IN (1, SIZE(RangeUpperBounds)) DO
            IF fix > RangeLowerBounds[r] AND fix <= RangeUpperBounds[r] THEN
                Payoff = Payoff + PAY(RangeLeverages[r] * FixingAmount * (fix - Strike), FixingDates[d], FixingDates[d], PayCcy);
            END;
        END;
    END;
END;
value = LongShort * Payoff;
\end{minted}
\caption{Accumulator Script}
\label{lst:accumulator_script}
\end{listing}

