\subsubsection{Equity Position}
\label{ss:equity_position}

An equity position represents a position in a single equity - using a single \lstinline!Underlying! node, or in a weighted basket of underlying equities -  using multiple \lstinline!Underlying! nodes. 

An Equity Position can be used both as a stand alone trade type (TradeType: \emph{EquityPosition}) or as a trade component ({\tt EquityPositionData}) used within the \emph{TotalReturnSwap} (Generic TRS) trade type, to set up for example Equity Basket trades.

 It is set up using an {\tt EquityPositionData} block as shown in listing \ref{lst:equitypositiondata}. The meanings and allowable
values of the elements in the block are as follows:

\begin{itemize}
\item Quantity: The number of shares or units of the weighted basket held.\\
  Allowable values: Any positive real number
\item Underlying: One or more underlying descriptions. If a basket of equities is defined, the \verb+Weight+ field
  should be populated for each underlyings. The weighted basket price is then given by\\
  $$\text{Basket-Price} = \text{Quantity} \times \sum_i \text{Weight}_i \times S_i \times \text{FX}_i$$
  where
  \begin{itemize}
  \item $S_i$ is the price of the ith share in the basket
  \item $FX_i$ is the FX Spot converting from the ith equity currency to the first equity currency which is by
    definition the currency in which the npv of the basket is expressed.
  \end{itemize}
  Allowable values: See \ref{ss:underlying} for the definition of an underlying. Only equity underlyings are allowed.
\end{itemize}

\begin{listing}[H]
\begin{minted}[fontsize=\footnotesize]{xml}
  <Trade id="EquityPosition">
    <TradeType>EquityPosition</TradeType>
    <Envelope>...</Envelope>
    <EquityPositionData>
      <Quantity>1000</Quantity>
        <Underlying>
          <Type>Equity</Type>
          <Name>BE0003565737</Name>
          <Weight>0.5</Weight>
          <IdentifierType>ISIN</IdentifierType>
          <Currency>EUR</Currency>
          <Exchange>XFRA</Exchange>
        </Underlying>
        <Underlying>
          <Type>Equity</Type>
          <Name>GB00BH4HKS39</Name>
          <Weight>0.5</Weight>
          <IdentifierType>ISIN</IdentifierType>
          <Currency>GBP</Currency>
          <Exchange>XLON</Exchange>
        </Underlying>
    </EquityPositionData>
  </Trade>
\end{minted}
\caption{Equity position data}
\label{lst:equitypositiondata}
\end{listing}