\subsubsection{Equity Auto Delta Hedged Option}

The \lstinline!EquityAutoDeltaHedgedOptionData! node is the trade data container for the
\emph{EquityAutoDeltaHedgedOption} trade type.  This trade type represents a structured
product consisting of one or more batches of European equity options with an embedded
discrete delta-hedging strategy.

The structure of an example \lstinline!EquityAutoDeltaHedgedOptionData! node is shown in
Listing \ref{lst:eqautodeltahedged_data}.

\begin{listing}[H]
\begin{minted}[fontsize=\footnotesize]{xml}
<EquityAutoDeltaHedgedOptionData>
  <Volatility>0.05</Volatility>
  <DriftRate>0.00</DriftRate>
  <Underlyings>
    <Underlying>
      <OptionData>
        <LongShort>Long</LongShort>
        <OptionType>Call</OptionType>
        <Style>European</Style>
        <Settlement>Cash</Settlement>
        <ExerciseDates>
          <ExerciseDate>2021-01-29</ExerciseDate>
        </ExerciseDates>
        <PremiumAmount>9.36</PremiumAmount>
        <PremiumCurrency>USD</PremiumCurrency>
        <PremiumPayDate>2019-03-01</PremiumPayDate>
      </OptionData>
      <Name>RIC:HSBA.L</Name>
      <Currency>USD</Currency>
      <Strike>3.5</Strike>
      <StrikeCurrency>USD</StrikeCurrency>
      <Quantity>51400</Quantity>
    </Underlying>
    <Underlying>
      ...
    </Underlying>
  </Underlyings>
  <ObservationStartDate>2020-11-11</ObservationStartDate>
</EquityAutoDeltaHedgedOptionData>
\end{minted}
\caption{Equity Auto Delta Hedged Option data}
\label{lst:eqautodeltahedged_data}
\end{listing}

The meanings and allowable values of the elements in the
\lstinline!EquityAutoDeltaHedgedOptionData! node follow below.

\begin{itemize}

\item \lstinline!Volatility! [Mandatory]:  The hedging volatility $\sigma_h$ used in the
  Black--Scholes delta computation for the daily delta-hedge rebalancing.
  Expressed as a decimal (e.g.\ \texttt{0.05} for 5\%).

  Allowable values: any non-negative real number.

\item \lstinline!DriftRate! [Mandatory]:  The continuously compounded rate $r$ used in the
  contractual forward formula $F_{t,T} = S_t \cdot e^{r\,\tau}$, where $\tau$ is the
  Actual/365~(Fixed) year fraction from observation date to expiry.

  Allowable values: any real number (typically \texttt{0.00}).

\item \lstinline!Underlyings! [Mandatory]:  A container node holding one or more
  \lstinline!Underlying! child nodes.  Each \lstinline!Underlying! defines a single batch
  of options within the auto delta hedged structure.

  \begin{itemize}

  \item \lstinline!OptionData!:  This is a trade component sub-node outlined in
    section~\ref{ss:option_data}.  The relevant fields are:

    \begin{itemize}
    \item \lstinline!LongShort!:  The allowable values are \emph{Long} or \emph{Short}.
    \item \lstinline!OptionType!:  The allowable values are \emph{Call} or \emph{Put}.
    \item \lstinline!Style!:  Must be \emph{European}.
    \item \lstinline!Settlement!:  Must be \emph{Cash}.
    \item An \lstinline!ExerciseDates! node with exactly one \lstinline!ExerciseDate!.
    \item \lstinline!PremiumAmount!, \lstinline!PremiumCurrency!, \lstinline!PremiumPayDate!:
      Exactly one premium per underlying is required.  The premium is included in the equity
      amount calculation at expiry.
    \end{itemize}

  \item \lstinline!Name! [Mandatory]:  The identifier of the underlying equity or equity index.

    Allowable values: See \lstinline!Name! for equity trades in Table~\ref{tab:equity_name}.

  \item \lstinline!Currency! [Mandatory]:  The payment currency.

    Allowable values: See \lstinline!Currency! in Table~\ref{tab:allow_stand_data}.

  \item \lstinline!Strike! [Mandatory]:  The option strike price.

    Allowable values: any positive real number.

  \item \lstinline!StrikeCurrency! [Optional]:  The currency of the strike.

    Allowable values: See \lstinline!Currency! in Table~\ref{tab:allow_stand_data}.

  \item \lstinline!Quantity! [Mandatory]:  The number of underlying options in this batch ($N^i$).

    Allowable values: any positive real number.

  \end{itemize}

\item \lstinline!ObservationStartDate! [Mandatory]:  The date from which the discrete
  delta-hedging observation begins.  Historical fixings of the equity index between the
  observation start date and the valuation date are used to compute the realized hedge P\&L.

  Allowable values: See \lstinline!Date! in Table \ref{tab:allow_stand_data}.

\end{itemize}
