\subsubsection{European Option Contingent on a Barrier}

European exercise, American or European barrier, multi-asset

This is a plain vanilla European option on a given underlying, whose final payoff is contingent on the
price level of another underlying (forming the barrier). Both underlyings can be of multiple asset classes.

The trade container for this product is the \verb+EuropeanOptionBarrierData+ node, and the corresponding
trade type is EuropeanOptionBarrier. The barrier can be continuously monitored (American) or only be
monitored on the option expiry date (European). Currently, we support Equity, FX, Commodity and InterestRate
for the option underlying. For the barrier underlying, we support Equity, FX, Commodity and InterestRate
for European-style barriers, but not InterestRate for an American-style barrier.

Listing \ref{lst:european_option_american_barrier} shows the structure of an Equity European option with
an American-style FX barrier. For a European-style barrier, the \lstinline!BarrierType! must be set
to \emph{European} and the \lstinline!BarrierSchedule! can be omitted.

\begin{listing}[H]
\begin{minted}[fontsize=\footnotesize]{xml} 
<Trade id="Equity_EuropeanOptionWithAmericanFxBarrier">
  <TradeType>EuropeanOptionBarrier</TradeType>
  <Envelope>
    .....
  </Envelope>
  <EuropeanOptionBarrierData>
    <Quantity>8523</Quantity>
    <PutCall>Call</PutCall>
    <LongShort>Short</LongShort>
    <Strike>3520</Strike>
    <PremiumAmount>114.40</PremiumAmount>
    <PremiumCurrency>EUR</PremiumCurrency>
    <PremiumDate>2019-12-13</PremiumDate>
    <OptionExpiry>2020-06-19</OptionExpiry>
    <OptionUnderlying>
      <Type>Equity</Type>
      <Name>RIC:.STOXX50E</Name>
    </OptionUnderlying>
    <BarrierUnderlying>
      <Type>FX</Type>
      <Name>ECB-EUR-USD</Name>
    </BarrierUnderlying>
    <BarrierLevel>1.09335</BarrierLevel>
    <BarrierType>DownAndIn</BarrierType>
    <BarrierStyle>American</BarrierStyle>
    <BarrierSchedule>
      <Rules>
        <StartDate>2019-12-11</StartDate>
        <EndDate>2020-06-19</EndDate>
        <Tenor>1D</Tenor>
        <Calendar>USA</Calendar>
        <Convention>Following</Convention>
        <TermConvention>Following</TermConvention>
        <Rule>Forward</Rule>
      </Rules>
    </BarrierSchedule>
    <SettlementDate>2020-06-24</SettlementDate>
    <PayCcy>USD</PayCcy>
  </EuropeanOptionBarrierData>
</Trade>
\end{minted}
\caption{European Option Barrier data (continuous barrier)}
\label{lst:european_option_american_barrier}
\end{listing}

The meanings and allowable values of the elements in the \lstinline!EuropeanOptionBarrierData! node follow below.
 
\begin{itemize} 
  \item Quantity: Number of option contracts. \\
  Allowable values: Any non-negative number.
  \item PutCall: Option type. \\
  Allowable values: \emph{Call, Put}
  \item LongShort: Own party position. \\
  Allowable values: \emph{Long, Short}
  \item Strike: Option strike price. \\
  Allowable values: Any positive number.
  \item PremiumAmount: Premium amount per option. \\
  Allowable values: Any number.
  \item PremiumCurrency: Currency of the option premium. \\
  Allowable values: See \lstinline!Currency! in Table \ref{tab:allow_stand_data}.
  \item PremiumDate: The option premium payment date. \\
  Allowable values: See \lstinline!Date! in Table \ref{tab:allow_stand_data}.
  \item OptionExpiry: Option expiry date. \\
  Allowable values: See \lstinline!Date! in Table \ref{tab:allow_stand_data}.
  \item OptionUnderlying: The option underlying. \\
  Allowable values: A node of the same form as \lstinline!Underlying!, (see \ref{ss:underlying}). The supported types
  are \emph{Equity}, \emph{FX}, \emph{Commodity} and \emph{InterestRate}. \\
  \item BarrierUnderlying: The underlying monitored against the barrier level. \\
  Allowable values: A node of the same form as \lstinline!Underlying!, (see \ref{ss:underlying}). The supported types
  are \emph{Equity}, \emph{FX}, \emph{Commodity} and \emph{InterestRate} if \lstinline!BarrierStyle! is \emph{European}. For \lstinline!BarrierStyle!
  \emph{American}, we only support \emph{Equity}, \emph{FX} and \emph{Commodity}.
  \item BarrierLevel: Knock-in/knock-out barrier level. \\
  Allowable values: Any number.
  \item BarrierType: The type of knock-in or knock-out barrier. \\
  Allowable values: \emph{DownIn, UpIn, DownOut, UpOut}
  \item BarrierStyle: Whether the barrier is continuously monitored or only at the option expiry date. \\
  Allowable values: \emph{American, European}
  \item BarrierSchedule [Optional]: The schedule specifying the schedule of trading days over which the continuous
  barrier will be monitored. This is required only when \lstinline!BarrierStyle! is \emph{American}. \\
  Allowable values: A node of the same form as \lstinline!ScheduleData!, (see \ref{ss:schedule_data}).
  \item SettlementDate: Settlement date of the option exercise payoff. \\
  Allowable values: See \lstinline!Date! in Table \ref{tab:allow_stand_data}. The Settlement date must be on or after the Option expiry date.
  \item PayCcy: Settlement currency. \\
  Allowable values: See Table \ref{tab:currency} \lstinline!Currency!.
\end{itemize}