\subsubsection{Forward Rate Agreement}

\ifdefined\IncludePayoff{{\bf Payoff}

A Forward Rate Agreement is a contract between two counterparties that determines 
a fixed forward interest rate benchmarked to a reference IBOR index rate and tenor. 
\begin{itemize}
\item Difference between the forward rate and the reference rate is to be 
paid/received at the end of the contract. 
\item Interest is accrued on a predetermined notional amount from an agreed upon 
start date to the end of the FRA contract.
\item There are no exchanges of notional.
\end{itemize}

{\bf Input}}\fi

A forward rate agreement (trade type \emph{ForwardRateAgreement} is set up using a \\
{\tt ForwardRateAgreementData} block as shown in listing \ref{lst:ForwardRateAgreementdata}. The forward rate agreement specific elements
are:

\begin{itemize}
\item StartDate: A FRA expires/settles on the startDate. \\

Allowable values:  See \lstinline!Date! in Table \ref{tab:allow_stand_data}.

\item EndDate: EndDate is the date when the forward loan or deposit ends. It follows that (EndDate - StartDate) is the tenor/term of the underlying loan or deposit.

Allowable values:  See \lstinline!Date! in Table \ref{tab:allow_stand_data}.
\item Currency: The currency of the FRA notional. \\

Allowable values:  See Table \ref{tab:currency} \lstinline!Currency!.	
\item Index: The name of the interest rate index the FRA is benchmarked against.

  Allowable values: An alphanumeric string of the form CCY-INDEX-TENOR. CCY, INDEX and TENOR must be separated by dashes (-). CCY and INDEX must be among the supported currency and index combinations. TENOR must be an integer followed by D, W,
  M or Y, except for Overnight indices which do not require a TENOR. See Table \ref{tab:indices}.
    
\item LongShort: Specifies whether the FRA position is long (one receives the agreed rate) or short (one pays the agreed rate).

Allowable values: \emph{Long}, \emph{Short}.
\item Strike: The agreed forward interest rate.

Allowable values: Any  real number. The strike rate is
  expressed in decimal form, e.g. 0.05 is a rate of 5\%.
\item Notional: No accretion or amortisation, just a constant notional. \\
Allowable values:  Any positive real number.
\end{itemize}


\begin{listing}[H]
%\hrule\medskip
\begin{minted}[fontsize=\footnotesize]{xml}
    <ForwardRateAgreementData>
        <StartDate>20161028</StartDate>
        <EndDate>20351028</EndDate>
        <Currency>EUR</Currency>
        <Index>EUR-EURIBOR-6M</Index>
        <LongShort>Long</LongShort>
        <Strike>0.001</Strike>
        <Notional>1000000000</Notional>
    </ForwardRateAgreementData>
\end{minted}
\caption{Forward Rate Agreement Data}
\label{lst:ForwardRateAgreementdata}
\end{listing}
