\subsubsection{FX Chooser KO Option}

\ifdefined\IncludePayoff{{\bf Payoff}

The FX Chooser KO Option documented here is implemented as a \emph{scripted trade} with three
FX underlyings. The script computes three candidate European-style payoffs at one expiry date and
applies a knock-out condition on a barrier observation schedule.

In the default regression test script (\lstinline!ChooserOption!), the candidate payoffs are:
\[
\mathrm{Payoff}_i = N \cdot \max\left(\frac{K_i - S_i(T)}{S_i(T)}, 0\right), \quad i=1,2,3
\]
where \(N\) is \lstinline!Notional!, \(K_i\) are \lstinline!Strike1..3!, and
\(S_i(T)\) are the corresponding FX index fixings at \lstinline!Expiry!.

The trade is knocked out (terminated) if, for any barrier observation date and any underlying,
the observed fixing is less than or equal to the corresponding \lstinline!KOLevels! value. If
knocked out, the selected payoff is zero. If not knocked out, the chooser selection logic applies
and the selected payoff is settled at \lstinline!Settlement! in \lstinline!PayCcy!.

{\bf Input}}

\else

European exercise, scripted multi-FX payoff with knock-out monitoring.

This trade is represented as a \lstinline!ScriptedTrade! and uses a custom
\lstinline!ChooserOptionData! payload consumed by a script named \lstinline!ChooserOption!.

\fi

The trade representation for this product is a \lstinline!ScriptedTrade!, see
Section \ref{app:scriptedtrade}. The trade payload node is
\lstinline!ChooserOptionData!. A representative input structure is shown in
Listing \ref{lst:fxchooserkooption_data}.

\begin{listing}[H]
\begin{minted}[fontsize=\footnotesize]{xml}
<Trade id="ChooserCurrencyKOOption">
	<TradeType>ScriptedTrade</TradeType>
	<Envelope>
		<CounterParty>CPTY_A</CounterParty>
		<NettingSetId>CPTY_A</NettingSetId>
		<AdditionalFields />
	</Envelope>
	<ChooserOptionData>
		<Premium type="number">10</Premium>
		<PremiumCcy type="currency">EUR</PremiumCcy>
		<PremiumDate type="event">2025-12-15</PremiumDate>
		<Expiry type="event">2026-02-23</Expiry>
		<Settlement type="event">2026-02-25</Settlement>
		<PayCcy type="currency">EUR</PayCcy>
		<Notional type="number">1111000</Notional>
		<Strike1 type="number">19.50</Strike1>
		<Strike2 type="number">1.70</Strike2>
		<Strike3 type="number">20.00</Strike3>
		<KOLevels type="number">
			<Value>15.00</Value>
			<Value>1.00</Value>
			<Value>15.555</Value>
		</KOLevels>
		<BarrierDates type="event">
			<ScheduleData>
				<Rules>
					<StartDate>2026-02-26</StartDate>
					<EndDate>2026-02-26</EndDate>
					<Tenor>1D</Tenor>
					<Convention>Following</Convention>
					<TermConvention>Following</TermConvention>
					<Calendar>USA</Calendar>
					<Rule>Forward</Rule>
				</Rules>
			</ScheduleData>
		</BarrierDates>
		<FXIndex type="index">
			<Value>FX-TR20H-EUR-ZAR</Value>
			<Value>FX-TR20H-EUR-AUD</Value>
			<Value>FX-TR20H-EUR-MXN</Value>
		</FXIndex>
		<isDeliverable type="number">
			<Value>1</Value>
			<Value>1</Value>
			<Value>1</Value>
		</isDeliverable>
		<LongShort type="number">1</LongShort>
	</ChooserOptionData>
</Trade>
\end{minted}
\caption{FX Chooser KO Option data (scripted representation)}
\label{lst:fxchooserkooption_data}
\end{listing}

The meanings and allowable values of the elements in the
\lstinline!ChooserOptionData! node are:

\begin{itemize}
	\item{}[number] \lstinline!Premium! [Optional]: Premium amount. In the default regression script,
		this field is informational unless explicitly referenced in a custom script. \\
		Allowable values: Any real number.

	\item{}[currency] \lstinline!PremiumCcy! [Optional]: Currency of \lstinline!Premium!. \\
		Allowable values: See Table \ref{tab:currency} \lstinline!Currency!.

	\item{}[event] \lstinline!PremiumDate! [Optional]: Premium payment date. \\
		Allowable values: See \lstinline!Date! in Table \ref{tab:allow_stand_data}.

	\item{}[event] \lstinline!Expiry!: Option expiry date used for candidate payoff evaluation. \\
		Allowable values: See \lstinline!Date! in Table \ref{tab:allow_stand_data}.

	\item{}[event] \lstinline!Settlement!: Option settlement date for the selected payoff. \\
		Allowable values: See \lstinline!Date! in Table \ref{tab:allow_stand_data}.

	\item{}[currency] \lstinline!PayCcy!: Settlement currency. \\
		Allowable values: See Table \ref{tab:currency} \lstinline!Currency!.

	\item{}[number] \lstinline!Notional!: Notional multiplier applied in each candidate payoff. \\
		Allowable values: Any positive real number.

	\item{}[number] \lstinline!Strike1!, \lstinline!Strike2!, \lstinline!Strike3!: Strike levels for
		the three candidate FX legs. \\
		Allowable values: Any positive real numbers.

	\item{}[number] \lstinline!KOLevels!: Ordered list of knock-out levels mapped one-to-one to the
		entries in \lstinline!FXIndex!. If any observed fixing is less than or equal to the corresponding
		KO level at an observation date, the trade is terminated. \\
		Allowable values: Positive real numbers.

	\item{}[event] \lstinline!BarrierDates!: Barrier observation schedule used for KO checks. \\
		Allowable values: A schedule node of the same form as \lstinline!ScheduleData!, see
		Section \ref{ss:schedule_data}.

	\item{}[index] \lstinline!FXIndex!: Ordered list of three FX indices used for payoff and KO
		evaluation. The list order maps to \lstinline!Strike1..3!, \lstinline!KOLevels! and
		\lstinline!isDeliverable! values. \\
		Allowable values: Valid FX index entries in the format
		\lstinline!FX-SOURCE-CCY1-CCY2! (Table \ref{tab:fxindex_data}).

	\item{}[number] \lstinline!isDeliverable!: Ordered list of three deliverability flags corresponding
		to the three FX legs. \\
		Allowable values: \emph{0} (not deliverable) or \emph{1} (deliverable).

	\item{}[number] \lstinline!LongShort!: Position sign as consumed by the scripted payoff. \\
		Allowable values: \emph{1} (long) or \emph{-1} (short).
\end{itemize}

The default script expects exactly three entries in \lstinline!FXIndex!,
\lstinline!KOLevels! and \lstinline!isDeliverable!, consistent with
\lstinline!Strike1..3!. If a different structure is required, update both the
trade payload and the corresponding script in the script library.
