\subsubsection{FX Chooser Option}

\ifdefined\IncludePayoff{{\bf Payoff}

The FX Chooser Option documented here is implemented as a \emph{scripted trade} with three
FX underlyings observed at one common expiry date. For each underlying, the script computes
an individual European-style payoff and then selects one leg according to deliverability and
moneyness rules.

In the default regression test script (\lstinline!ChooserOption!), the per-leg payoff is:
\[
\mathrm{Payoff}_i = N \cdot \max\left(\frac{K_i - S_i(T)}{S_i(T)}, 0\right), \quad i=1,2,3
\]
where \(N\) is \lstinline!Notional!, \(K_i\) are \lstinline!Strike1..3!, and
\(S_i(T)\) are the corresponding FX index fixings at \lstinline!Expiry!.

The selected payoff is paid at \lstinline!Settlement! in \lstinline!PayCcy!.

{\bf Input}}

\else

European exercise, scripted multi-FX payoff.

This trade is represented as a \lstinline!ScriptedTrade! and uses a custom
\lstinline!ChooserOptionData! payload consumed by a script named \lstinline!ChooserOption!.

\fi

The trade representation for this product is a \lstinline!ScriptedTrade!, see
Section \ref{app:scriptedtrade}. The trade payload node is
\lstinline!ChooserOptionData!. A representative input structure is shown in
Listing \ref{lst:fxchooseroption_data}.

\begin{listing}[H]
\begin{minted}[fontsize=\footnotesize]{xml}
<Trade id="ChooserCurrencyOption">
	<TradeType>ScriptedTrade</TradeType>
	<Envelope>
		<CounterParty>CPTY_A</CounterParty>
		<NettingSetId>CPTY_A</NettingSetId>
		<AdditionalFields />
	</Envelope>
	<ChooserOptionData>
		<Premium type="number">1</Premium>
		<PremiumCcy type="currency">EUR</PremiumCcy>
		<PremiumDate type="event">2025-12-01</PremiumDate>
		<Expiry type="event">2026-05-10</Expiry>
		<Settlement type="event">2026-05-12</Settlement>
		<PayCcy type="currency">EUR</PayCcy>
		<Notional type="number">100000</Notional>
		<Strike1 type="number">20.00</Strike1>
		<Strike2 type="number">20.00</Strike2>
		<Strike3 type="number">5.00</Strike3>
		<FXIndex type="index">
			<Value>FX-TR20H-EUR-CZK</Value>
			<Value>FX-TR20H-EUR-ZAR</Value>
			<Value>FX-TR20H-EUR-PLN</Value>
		</FXIndex>
		<isDeliverable type="number">
			<Value>1</Value>
			<Value>1</Value>
			<Value>1</Value>
		</isDeliverable>
		<LongShort type="number">1</LongShort>
	</ChooserOptionData>
</Trade>
\end{minted}
\caption{FX Chooser Option data (scripted representation)}
\label{lst:fxchooseroption_data}
\end{listing}

The meanings and allowable values of the elements in the
\lstinline!ChooserOptionData! node are:

\begin{itemize}
	\item{}[number] \lstinline!Premium! [Optional]: Premium amount. In the default regression script,
		this field is informational unless explicitly referenced in a custom script. \\
		Allowable values: Any real number.

	\item{}[currency] \lstinline!PremiumCcy! [Optional]: Currency of \lstinline!Premium!. \\
		Allowable values: See Table \ref{tab:currency} \lstinline!Currency!.

	\item{}[event] \lstinline!PremiumDate! [Optional]: Premium payment date. \\
		Allowable values: See \lstinline!Date! in Table \ref{tab:allow_stand_data}.

	\item{}[event] \lstinline!Expiry!: Option expiry/observation date. \\
		Allowable values: See \lstinline!Date! in Table \ref{tab:allow_stand_data}.

	\item{}[event] \lstinline!Settlement!: Option settlement date for the selected payoff. \\
		Allowable values: See \lstinline!Date! in Table \ref{tab:allow_stand_data}.

	\item{}[currency] \lstinline!PayCcy!: Settlement currency. \\
		Allowable values: See Table \ref{tab:currency} \lstinline!Currency!.

	\item{}[number] \lstinline!Notional!: Notional multiplier applied in each candidate payoff. \\
		Allowable values: Any positive real number.

	\item{}[number] \lstinline!Strike1!, \lstinline!Strike2!, \lstinline!Strike3!: Strike levels for
		the three candidate FX legs. \\
		Allowable values: Any positive real numbers.

	\item{}[index] \lstinline!FXIndex!: Ordered list of three FX indices used for payoff evaluation at
		expiry. The list order maps to \lstinline!Strike1..3! and \lstinline!isDeliverable! values. \\
		Allowable values: Valid FX index entries in the format
		\lstinline!FX-SOURCE-CCY1-CCY2! (Table \ref{tab:fxindex_data}).

	\item{}[number] \lstinline!isDeliverable!: Ordered list of three deliverability flags corresponding
		to the three FX legs. \\
		Allowable values: \emph{0} (not deliverable) or \emph{1} (deliverable).

	\item{}[number] \lstinline!LongShort!: Position sign as consumed by the scripted payoff. \\
		Allowable values: \emph{1} (long) or \emph{-1} (short).
\end{itemize}

The default script expects exactly three entries in \lstinline!FXIndex! and
\lstinline!isDeliverable!, consistent with \lstinline!Strike1..3!. If a different
structure is required, update both the trade payload and the corresponding
script in the script library.
