\subsubsection{FX Swap}

\ifdefined\IncludePayoff{{\bf Payoff}

An FX Swap is a contract that involves the exchange of a set amount of one 
currency for another at the start of the contract, and then the reverse exchange 
at the end of the contract. The exchange at the start uses the FX spot rate, 
whereas the exchange at the end uses the FX forward rate at the start. 

{\bf Input}}\fi

The \lstinline!FXSwapData!  node is the trade data container for the \emph{FxSwap} trade type.  The structure -
including example values - of the \lstinline!FXSwapData!  node is shown in Listing 
\ref{lst:fxswap_data}. 
It contains no sub-nodes.

\begin{listing}[H]
%\hrule\medskip
\begin{minted}[fontsize=\footnotesize]{xml}
        <FxSwapData>
            <NearDate>2018-09-01</NearDate>
            <NearBoughtCurrency>EUR</NearBoughtCurrency>
            <NearBoughtAmount>1000000</NearBoughtAmount>
            <NearSoldCurrency>USD</NearSoldCurrency>
            <NearSoldAmount>1140000</NearSoldAmount>
            <FarDate>2028-09-01</FarDate>
            <FarBoughtAmount>1300000</FarBoughtAmount>
            <FarSoldAmount>1000000</FarSoldAmount>
            <Settlement>Cash</Settlement>
        </FxSwapData>
\end{minted}
\caption{FX Swap data}
\label{lst:fxswap_data}
\end{listing}

The meanings and allowable values of the various elements in the \lstinline!FXSwapData!  node follow below.  All elements are required.

\begin{itemize}
\item NearDate: The date of the initial fx exchange of the FX Swap. \\ Allowable values:  See \lstinline!Date! in Table \ref{tab:allow_stand_data}.
\item NearBoughtCurrency: The currency to be bought in the initial exchange at near date, and sold in the final exchange at far date.  \\ Allowable values:  See Table \ref{tab:currency} \lstinline!Currency!.
\item NearBoughtAmount: The amount to be bought on near date.  \\ Allowable values:  Any positive real number.
\item NearSoldCurrency: The currency to be sold in the initial fx exchange at near date, and bought in the final exchange at far date.   \\ Allowable values:  See Table \ref{tab:currency} \lstinline!Currency!.
\item NearSoldAmount: The amount to be sold on near date.  \\ Allowable values:  Any positive real number.
\item FarDate: The date of the final fx exchange of the FX Swap. \\ Allowable values:  Any date further into the future than NearDate. See \lstinline!Date! in Table  \ref{tab:allow_stand_data}.
\item FarBoughtAmount: The amount to be bought on far date.  \\ Allowable values:  Any positive real number.
\item FarSoldAmount: The amount to be sold on far date.  \\ Allowable values:  Any positive real number.
\item Settlement [Optional]: Delivery type.  Note that Non-Deliverable FX Swaps can be represented by \emph{Cash} settlement, and that deliverable FX Swaps will be excluded from the CRIF output. Delivery type does not impact pricing in ORE.  

Allowable values: \emph{Cash} or \emph{Physical}.  Defaults to \emph{Physical} if left blank or omitted.

\end{itemize}

Note that FX Swaps also cover Precious Metals swaps, i.e. with currencies XAU, XAG, XPT, XPD, and Cryptocurrency swaps,  see supported Cryptocurrencies in Table \ref{tab:currency}.
