\subsubsection{Performance Option Type 01}

The performace option of type ``01'' is characterized by the following data

\begin{itemize}
\item a notional amount $N$
\item a participation rate $q$
\item a valuation date $V$ and a settlement date $S$
\item a number of underlyings $U_i$ for $i=1,\ldots,n$
\item weights for the underlyings $w_i$ for $i=1,\ldots,n$
\item initial strike prices for the underlyings $s_i$ for $i=1,\ldots,n$
\item an option strike $K$
\end{itemize}

On the valuation date the average performance of the underlying basket is computed as

$$
P = \max\left( \sum_{i=1}^n w_i \left( \frac{U_i(V)}{s_i} - K \right), 0 \right)
$$

The option holder receives an amount $N\cdot q\cdot P$ on the settlement date $S$. The underlyings can be Equity, FX or
Commodity underlyings.

The above payoff includes the strike in the performance calculation. There is another variant with excluded strike and payoff:

$$
P = \max\left( \left[ \sum_{i=1}^n w_i \frac{U_i(V)}{s_i} \right] - K, 0 \right)
$$

The \verb+PerformanceOption_01+ node is the trade data container for the PerformanceOption\_01 trade type, listing
\ref{lst:performanceoption01_data} shows the structure of an example.

\begin{listing}[H]
\begin{minted}[fontsize=\footnotesize]{xml}
    <PerformanceOption01Data>
      <NotionalAmount>12500000</NotionalAmount>
      <ParticipationRate>0.9</ParticipationRate>
      <ValuationDate>2022-05-03</ValuationDate>
      <SettlementDate>2022-05-05</SettlementDate>
      <Underlyings>
        <Underlying>
          <Type>FX</Type>
          <Name>ECB-CHF-EUR</Name>
          <Weight>0.34</Weight>
        </Underlying>
        <Underlying>
          <Type>FX</Type>
          <Name>ECB-NOK-EUR</Name>
          <Weight>0.32</Weight>
        </Underlying>
        <Underlying>
          <Type>FX</Type>
          <Name>ECB-SEK-EUR</Name>
          <Weight>0.24</Weight>
        </Underlying>
        <Underlying>
          <Type>FX</Type>
          <Name>ECB-SEK-EUR</Name>
          <Weight>0.10</Weight>
        </Underlying>
      </Underlyings>
      <StrikePrices>
        <StrikePrice>0.910002</StrikePrice>
        <StrikePrice>0.097192</StrikePrice>
        <StrikePrice>0.096085</StrikePrice>
        <StrikePrice>0.035032</StrikePrice>
      </StrikePrices>
      <Strike>1.15</Strike>
      <StrikeIncluded>true</StrikeIncluded>
      <Position>Long</Position>
      <PayCcy>EUR</PayCcy>
    </PerformanceOption01Data>
\end{minted}
\caption{Performance Option Type 01 data}
\label{lst:performanceoption01_data}
\end{listing}

The meanings and allowable values of the elements in the \verb+PerformanceOption01Data+  node follow below.

\begin{itemize}
\item NotionalAmount: The notional amount of the option. Allowable valus are non-negative numbers.
\item ParticipationRate: The participation rate. Allowable values are non-negative numbers. Usually the value will be
  between 0 and 1.
\item ValuationDate: The valuation date.  Allowable values are valid dates.
\item SettlementDate: The settlement date. Allowable values are valid dates.
\item Underlyings: The underlyings of the option. See \ref{ss:underlying} for each underlying.
\item StrikePrices: The initial strike prices of the underlyings. For an FX underlying FX-SOURCE-CCY1-CCY2 this is the
  number of units of CCY2 per units of CCY1. For an EQ underlying this is the equity price expressed in the equity ccy. For a Commodity underlying this is the commodity price quoted as per the underlying commodity.
  Allowable values are non-negative numbers.
\item Strike: The option strike. This is expressed in terms of the performance of the underlying basket (see the product
  description for more details). Allowable values are numbers.
\item StrikeIncluded [optional]: If true the strike is included in the performance calculation, this is also the default
  if the flag not given. If false the strike is excluded. 
\item Position: The option position. Allowable values are {\em Long} or {\em Short}.
\item PayCcy: The payment currency of the option. See the appendix for allowable currency codes.
\end{itemize}
