\subsubsection{Rate Digital Option}

A Rate Digital Option is a European cash-or-nothing option on an interest rate fixing. It pays a fixed cash amount if the
underlying rate index fixing on the fixing date is above the strike (Call) or below the strike (Put). This trade type is
useful for hedging or replicating Range Accrual coupons, where each daily observation can be decomposed into a digital
option on the rate.

The \lstinline!RateDigitalOptionData! node is the trade data container for the \emph{RateDigitalOption} trade type. It
includes one \lstinline!OptionData! trade component sub-node plus elements specific to the Rate Digital Option. The
structure of an example \lstinline!RateDigitalOptionData! node is shown in Listing
\ref{lst:ratedigitaloption_data}.

\begin{listing}[H]
%\hrule\medskip
\begin{minted}[fontsize=\footnotesize]{xml}
    <RateDigitalOptionData>
      <OptionData>
        <LongShort>Long</LongShort>
        <OptionType>Call</OptionType>
        <ExerciseDates>
          <ExerciseDate>2027-06-20</ExerciseDate>
        </ExerciseDates>
      </OptionData>
      <Index>EUR-EURIBOR-6M</Index>
      <Strike>0.02</Strike>
      <PayoffAmount>10000.0</PayoffAmount>
      <PayoffCurrency>EUR</PayoffCurrency>
      <FixingDate>2027-06-18</FixingDate>
      <PaymentDate>2027-06-20</PaymentDate>
    </RateDigitalOptionData>
\end{minted}
\caption{Rate Digital Option data}
\label{lst:ratedigitaloption_data}
\end{listing}

The meanings and allowable values of the elements in the \lstinline!RateDigitalOptionData! node follow below.

\begin{itemize}

\item OptionData: This is a trade component sub-node outlined in section \ref{ss:option_data}.
The relevant fields in the \lstinline!OptionData! node for a RateDigitalOption are:

\begin{itemize}
\item \lstinline!LongShort!: The allowable values are \emph{Long} or \emph{Short}.

\item \lstinline!OptionType!: \emph{Call} means that the digital payout occurs if the rate fixing is above the strike.
  \emph{Put} means that the digital payout occurs if the rate fixing is below the strike.

\item \lstinline!Style!: Only \emph{European} exercise style is supported (default if omitted).

\item An \lstinline!ExerciseDates! node where exactly one \lstinline!ExerciseDate! element must be given.

\item Premiums [Optional]: See section \ref{ss:premiums}.
\end{itemize}

\item Index: The underlying interest rate index whose fixing is observed.

  Allowable values: An alphanumeric string of the form CCY-INDEX-TENOR. Both Ibor indices (e.g.\ \emph{EUR-EURIBOR-6M})
  and overnight indices (e.g.\ \emph{USD-SOFR}) are supported. See Table \ref{tab:indices}.

\item Strike: The strike rate level for the digital condition.

  Allowable values: A positive real number, expressed in decimal form, e.g.\ \emph{0.02} is a strike of 2\%.

\item PayoffAmount: The fixed cash amount paid if the option expires in-the-money.

  Allowable values: A positive real number.

\item PayoffCurrency: The currency of the payoff amount.

  Allowable values: See Table \ref{tab:currency} \lstinline!Currency!.

\item FixingDate: The date on which the rate index fixing is observed.

  Allowable values: See \lstinline!Date! in Table \ref{tab:allow_stand_data}.

\item PaymentDate [Optional]: The date on which the payoff is settled. If omitted, defaults to the exercise date.

  Allowable values: See \lstinline!Date! in Table \ref{tab:allow_stand_data}.

\end{itemize}
