\subsubsection{Swap}\label{ss:swap}

\ifdefined\IncludePayoff{{\bf Payoff}

An interest rate swap ({\bf IRS}) is an agreement between two counterparties in which one 
stream of future interest payments (leg) is exchanged for another based on a 
specified notional amount. A vanilla interest rate swap involves two legs in 
the same currency, exchanging a floating rate benchmarked to an Interbank 
Offered Rate (IBOR)\footnote{IBOR is a generic term for a family of indices 
that represent a rate for deposit periods, or tenors, longer than one day. 
Specific IBOR indices are usually named after the location where they are set, 
such as LIBOR (London), TIBOR (Tokyo) or EURIBOR (Eurozone).}   
index of a specified tenor for a fixed rate, or vice versa. 
\begin{itemize}
\item The notional amount for each leg may be fixed, amortising or accreting. 
\item The fixed rate and the spread can vary over the lifetime of the swap. 
\end{itemize} 

A single currency basis swap ({\bf BS}) has two floating legs, benchmarked to any two of 
the supported IBOR indices. The two legs may also have different tenors of the 
same IBOR index. 
\begin{itemize}
\item The notional amount for each leg may be fixed, amortising or accreting. 
\item The floating leg spreads can vary over the lifetime of the swap. 
\end{itemize}

An Overnight Index Swap ({\bf OIS}) has at least one leg where the floating rate is 
benchmarked to an overnight index rate, typically the rate for overnight unsecured 
lending between banks. 
\begin{itemize}
\item For example, in USD the overnight index rate would be the Federal Funds rate, 
in EUR it would be Eonia, and in GBP it would be Sonia. 
\item The overnight index rate leg compounds on a daily basis as per the corresponding
overnight rate.
\end{itemize}
The typical OIS Swap exchanges compounded overnight interest for a fixed leg, paying 
once at maturity for maturities up to a year and paying annually for longer maturities.
In the US OIS Swap market another flavour is common that exchanges an OIS linked leg 
paying the arithmetic weighted average of O/N fixings (quarterly, without compounding)  
for a floating USD-LIBOR-3M linked leg with a spread.

A Bond Market Association ({\bf BMA}) Swap has at least one leg where the floating rate 
is benchmarked to the BMA's floating rate municipal swap index. That is, 
the floating leg rate is based upon fixings of the US SIFMA Municipal Swap Index 
(formerly the BMA Municipal Index or ``BMA Index''). The non-BMA leg of a BMA Swap 
can be fixed or floating.

A Constant Maturity Swap ({\bf CMS}) has at least one leg where the floating rate is 
benchmarked against a CMS index using the market rate of a fixed maturity 
instrument, such as a swap, with a longer maturity than the 
length of the reset period. The CMS leg may contain a cap, floor, or collar. 

Similar to a CMS, a variable rate Swap leg can be linked to a Constant Maturity Bond ({\bf CMB}) index.
In contrast to CMS the yield is determined by the yields of a class of Bonds, such as Government Bonds.
As in the CMS case, the term of the yield is typically longer than the length of the reset period.
A CMB index in ORE is of the form CMB-FAMILY-TENOR.
Note, that the CMB linked legs in ORE currently do not support Caps, Floors or Collars.

{\bf Input}}\fi

The \lstinline!SwapData! node is the trade data container for the \emph{Swap} trade type. A Swap must have at least one leg,
and can have an unlimited number of legs. Each leg is represented by a \lstinline!LegData! trade component sub-node,
described in section \ref{ss:leg_data}. An example structure of a two-legged \lstinline!SwapData!
node is shown in Listing \ref{lst:swap_data}.
\begin{itemize}
\item Settlement [Optional]: Delivery type applicable to cross currency swaps, and ignored for all other swap types. Delivery type does not impact pricing in ORE, but npv results are produced with and without SIMM exemptions.  

Settlement \emph{Cash} indicates that principal exchanges on the cross currency swap should be included in Initial Margin (IM). According to ISDA non-deliverable (\emph{Cash}) trades are excluded from the exemption from IM for the principal exchange, i.e. the principal exchanges are included in IM. 

Settlement \emph{Physical} indicates that principal exchanges on the cross currency swap should be excluded in IM (the ISDA exemption applies).  

Allowable values: \emph{Cash} or \emph{Physical}.  Defaults to \emph{Physical} if left blank or omitted.
\end{itemize}

\begin{listing}[H]
%\hrule\medskip
\begin{minted}[fontsize=\footnotesize]{xml}
<SwapData>
  <Settlement>Cash</Settlement>
  <LegData>
    ...
  </LegData>
  <LegData>
    ...
  </LegData>
</SwapData>
\end{minted}
\caption{Swap data}
\label{lst:swap_data}
\end{listing}


Note that Swaps in non-deliverable currencies with payment in a deliverable currency are supported by setting Settlement  to \emph{Cash} and - on both legs - using the Indexings node (\ref{ss:indexings}), as well as setting the Currency to the deliverable currency, while keeping the Notional expressed in the non-deliverable currency amount. 

Within the  Indexings node,  an fx Index field is mandatory defining the deliverable and non-deliverable currencies and fixing source. The Indexing node can also include optional FixingCalendar, IsInArrears and FixingDays fields to determine the date(s) of the fx fixing(s). See Listing \ref{lst:ndir_swap} for an example non-deliverable IR swap where USD is the payment currency and CLP is the non-deliverable currency.


\begin{listing}[H]
%\hrule\medskip
\begin{minted}[fontsize=\footnotesize]{xml}
<SwapData>
  <Settlement>Cash</Settlement>
  <LegData>
   <LegType>Fixed</LegType>
   <Payer>false</Payer>  
   <Currency>USD</Currency><!-- Payment currency is USD rather than CLP -->
    <Notionals>
     <Notional>850000000</Notional><!-- in CLP -->
    </Notionals>
    <Indexings>
      <Indexing>
	<Index>FX-TR20H-CLP-USD</Index><!-- to convert CLP flows into USD -->
	<FixingCalendar>CLP,USD</FixingCalendar>
        <IsInArrears>true</IsInArrears>
        <FixingDays>2</FixingDays>
      </Indexing>
    </Indexings> 
    ...
  </LegData>
  <LegData>
   <LegType>Floating</LegType>
   <Payer>true</Payer>  
   <Currency>USD</Currency><!-- Payment currency is USD rather than CLP -->
    <Notionals>
     <Notional>850000000</Notional><!-- in CLP -->
     </Notionals>
     <Indexings>
      <Indexing>
	<Index>FX-TR20H-CLP-USD</Index><!-- to convert CLP flows into USD -->
	<FixingCalendar>CLP,USD</FixingCalendar>
        <IsInArrears>true</IsInArrears>
        <FixingDays>2</FixingDays>
      </Indexing>
     </Indexings>     
    ...    
  </LegData>
</SwapData>
\end{minted}
\caption{Non deliverable single currency IR Swap}
\label{lst:ndir_swap}
\end{listing}
