\subsubsection{Window Barrier Option}

The \verb+FxWindowBarrierOptionData+, \verb+EquityWindowBarrierOptionData+, \verb+CommodityWindowBarrierOptionData+ is
the trade data container for the FxWindowBarrierOption, EquityWindowBarrierOption, CommodityBarrierOption trade
type. The following listing shows the structure of an example trade for an FX underlying.

\begin{minted}[fontsize=\footnotesize]{xml}
<Trade id="FX_Window_BarrierOption">
  <TradeType>FxWindowBarrierOption</TradeType>
  <Envelope>
   ...
  </Envelope>
  <FxWindowBarrierOptionData>
    <Currency>USD</Currency>
    <FixingAmount>1000000</FixingAmount>
    <Underlying>
      <Type>FX</Type>
      <Name>ECB-EUR_USD</Name>
    </Underlying>
    <Strike>1.1</Strike>
    <StartDate>2023-03-01</StartDate>
    <EndDate>024-03-01</EndDate>
    <OptionData>
      <LongShort>Long</LongShort>
      <OptionType>Call</OptionType>
      <ExerciseDates>
        <ExerciseDate>2026-03-01</ExerciseDate>
      </ExerciseDates>
      <Premiums>
        <Premium>
          <Amount>10900</Amount>
          <Currency>EUR</Currency>
          <PayDate>2018-03-01</PayDate>
        </Premium>
      </Premiums>
      <PaymentData>
        <Dates>
          <Date>2026-03-01</Date>
        </Dates>
      </PaymentData>
    </OptionData>
    <BarrierData>
      <Type>UpAndOut</Type>
      <Levels>
        <Level>1.3</Level>
      </Levels>
    </BarrierData>
  </FxWindowBarrierOptionData>
</Trade>
\end{minted}

The meanings and allowable values of the elements in the data node follow below.

\begin{itemize}

\item Currency: The payout currency. The result of the payout formula above is treated to be in this currency. Note that
  for (non-quanto) FxWindowBarrierOption this should be the domestic (\lstinline!CCY2!) currency. For non-quanto Equity-
  and CommodityWindowBarrierOptions this should be the currency the equity or commodity is quoted in.
  Notice section ``Payment Currency'' in ore/Docs/ScriptedTrade. \\

Allowable values: See Table \ref{tab:currency} \lstinline!Currency!.

\item FixingAmount: The notional amount. For FxWindowBarrierOptions: The FixingAmount is expressed in the foreign currency
  (\lstinline!CCY1!).  For EquityWindowBarrierOptions: The FixingAmount is expressed as number of shares/units of the underlying
  equity or equity index. For CommodityWindowBarrierOptions: The FixingAmount is expressed as number of units of the underlying
  commodity. \\

Allowable values: Any positive real number.

\item Underlying: A node with the underlying of the Window Barrier instrument. For FxWindowBarrierOption:
  \lstinline!Type! is set to \emph{FX} and \lstinline!Name! is a string of the form \emph{SOURCE-CCY1-CCY2} where
  \lstinline!CCY1! is the foreign currency, \lstinline!CCY2! is the domestic currency, and \emph{SOURCE} is the fixing
  source, see Table \ref{tab:fxindex_data} and \ref{ss:underlying}. For EquityWindowBarrierOption: \lstinline!Type! is
  set to \emph{Equity} and \lstinline!Name! and other fields are as outlined in \ref{ss:underlying}. For
  CommodityWindowBarrierOption: \lstinline!Type! is set to \emph{Commodity} and \lstinline!Name! is an identifier of the
  commodity as outlined in \ref{ss:underlying} and in Table \ref{tab:commodity_data}.\\

Allowable values: Any FX, Equity or Commodity underlying as specified in \ref{ss:underlying}

\item StrikeData [Optional]: A node containing the strike in \lstinline!Value! and the currency in which both the
  underlying and the strike are quoted in \lstinline!Currency!. Only supported for EquityWindowBarrierOption.\\

Allowable values: See \lstinline!Currency! in Table \ref{tab:allow_stand_data}. The strike may be any positive real
number. The currency provided in this node may be quoted as corresponding minor currency to the underlying major
currency.

\item Strike [Optional]: For FxWindowBarrierOptions: The the fx strike rate is defined as amount in domestic currency
  (\lstinline!CCY2!) for one unit of foreign currency (\lstinline!CCY1!). For Equity- and CommodityWindowBarrierOptions: The
  strike value for one unit/share/contract of the underlying equity or commodity, expressed in the currency the equity
  or commodity is quoted in. For EquityWindowBarrierOptions, the \lstinline!StrikeData! node (see above) should be used. \\

Allowable values: Any positive real number.

\item StartDate: The start date of the continuous observation window.\\

Allowable values: Any valid date.

\item EndDate: The end date of the continuous observation window.\\

Allowable values: Any valid date.

\item OptionData: See \ref{ss:option_data}. The relevant fields in the \lstinline!OptionData! node for a Window Barrier Option are:

\begin{itemize}
\item \lstinline!LongShort! The allowable values are \emph{Long} or \emph{Short}.
\item \lstinline!OptionType! The allowable values are \emph{Call} or \emph{Put}.
\item \lstinline!ExerciseDates! Must contain the single exercise date of the option.
\item \lstinline!Premiums! [Optional] Option premium amounts paid by the option buyer to the option seller. See section \ref{ss:premiums}
\item \lstinline!PaymentData! [Optional] Optional pay date associated to the exercise date.
\end{itemize}

\item BarrierData: Specification of the barrier type and level. The barrier is continuosly monitored between the
  StartDate and EndDate. \\

Allowable values: See \ref{ss:barrier_data}, allowable types are \emph{UpAndOut}, \emph{DownAndOut},\emph{UpAndIn},
\emph{DownAndIn}. Exactly one level must be given as a positive real number.

\end{itemize}

% alternative representation as scripts

Window Barrier Options can be alternatively represented as {\em scripted trades}, refer to ore/Docs/ScriptedTrade
for an introduction.

Trade input and the payoff script are described below.

\begin{minted}[fontsize=\footnotesize]{xml}
<Trade id="WindowBarrierOption#1">
  <TradeType>ScriptedTrade</TradeType>
  <Envelope/>
  <WindowBarrierOptionData>
    <PremiumPayDate type="event">2018-03-01</PremiumPayDate>
    <Settlement type="event">2026-03-01</Settlement>
    <Expiry type="event">2026-03-01</Expiry>
    <StartDate type="event">2023-03-01</StartDate>
    <EndDate type="event">2024-03-01</EndDate>
    <PremiumAmount type="number">10900</PremiumAmount>
    <BarrierLevel type="number">1.3</BarrierLevel>
    <PutCall type="optionType">Call</PutCall>
    <BarrierType type="barrierType">UpOut</BarrierType>
    <LongShort type="longShort">Long</LongShort>
    <Quantity type="number">1000000</Quantity>
    <Strike type="number">1.1</Strike>
    <PayCcy type="currency">USD</PayCcy>
    <PremiumCcy type="currency">EUR</PremiumCcy>
    <Underlying type="index">FX-ECB-EUR-USD</Underlying>
  </WindowBarrierOptionData>
</Trade>
\end{minted}

The WindowBarrierOption script referenced in the trade above is
shown in Listing \ref{lst:windowbarrieroption}.

\begin{listing}[hbt]
\begin{minted}[fontsize=\footnotesize]{Basic}
REQUIRE BarrierType == 1 OR BarrierType == 2 OR BarrierType == 3 OR BarrierType == 4;

NUMBER i, Payoff, TriggerProbability, ExerciseProbability, isUp, currentNotional;

IF BarrierType == 1 OR BarrierType == 3 THEN
  TriggerProbability = BELOWPROB(Underlying, StartDate, EndDate, BarrierLevel);
ELSE
  TriggerProbability = ABOVEPROB(Underlying, StartDate, EndDate, BarrierLevel);
END;

Payoff = Quantity * PutCall * (Underlying(Expiry) - Strike);
IF Payoff > 0.0 THEN
  IF BarrierType == 1 OR BarrierType == 2 THEN
    Option = PAY(Payoff * TriggerProbability, Expiry, Settlement, PayCcy);
    ExerciseProbability = TriggerProbability;
  ELSE
    Option = PAY(Payoff * (1 - TriggerProbability), Expiry, Settlement, PayCcy);
    ExerciseProbability = (1 - TriggerProbability);
  END;
END;

Option = LongShort * (Option - PAY(PremiumAmount, PremiumPayDate, PremiumPayDate, PremiumCcy));
currentNotional = Quantity * Strike;
\end{minted}
\caption{Payoff script for a WindowBarrierOption.}
\label{lst:windowbarrieroption}
\end{listing}

The meanings and allowable values of the elements in the \lstinline!WindowBarrierOptionData! node below.

\begin{itemize}
    \item{}[event] \lstinline!Expiry!: Option expiry date. \\
    Allowable values: See \lstinline!Date! in Table \ref{tab:allow_stand_data}.
    \item{}[event] \lstinline!Settlement!: Option settlement date. \\
    Allowable values: See \lstinline!Date! in Table \ref{tab:allow_stand_data}.
    \item{}[event] \lstinline!StartDate!: Barrier monitoring start date. \\
    Allowable values: See \lstinline!Date! in Table \ref{tab:allow_stand_data}.
    \item{}[event] \lstinline!EndDate!: Barrier monitoring start date. \\
    Allowable values: See \lstinline!Date! in Table \ref{tab:allow_stand_data}.
    \item{}[number] \lstinline!Strike!: The option strike price. For FX, this should be the amount of \lstinline!CCY1! divided by amount of \lstinline!CCY2! as defined in \emph{Index}. \\
    Allowable values: Any positive real number.
    \item{}[number] \lstinline!BarrierLevel!: Knock-in or knock-out barrier level. For FX, this should be quoted as amount of \lstinline!CCY2! per unit \lstinline!CCY1! as defined in \emph{Index}. \\
    Allowable values: Any positive real number.
    \item{}[barrierType] \lstinline!BarrierType!: Barrier type. \\
    Allowable values: \emph{DownIn, UpIn, DownOut, UpOut}
    \item{}[optionType] \lstinline!PutCall!: Option type. For FX, this should be Call if we buy \lstinline!CCY1! and sell \lstinline!CCY2!, Put if we buy \lstinline!CCY2! and sell \lstinline!CCY1! (with \lstinline!CCY1!, \lstinline!CCY2! defined in \emph{Index}). \\
    Allowable values: \emph{Call, Put}
    \item{}[longShort] \lstinline!LongShort!: \emph{Long} if we buy the option. \emph{Short} if we sell the option.
    Allowable values: \emph{Long, Short}
    \item{}[number] \lstinline!Quantity!: Number of option contracts. For FX, this should be the bought amount. \\
    Allowable values: Any positive real number.
    \item{}[index] \lstinline!Underlying!: Underlying index. \\
    Allowable values: See ore/Docs/ScriptedTrade's Index Section for allowable values.
    \item{}[currency] \lstinline!PayCcy!: The payment currency. For FX, where the underlying is provided
      in the form \lstinline!FX-SOURCE-CCY1-CCY2! (see Table \ref{tab:fxindex_data}) this should
      be \lstinline!CCY2!. If \lstinline!CCY1! or the currency of the underlying (for EQ and
      COMM underlyings), this will result in a quanto payoff. Notice section ``Payment Currency'' in ore/Docs/ScriptedTrade. \\
        Allowable values: See Table \ref{tab:currency} for allowable currency codes.
    Allowable values: See \lstinline!Currency! in Table \ref{tab:allow_stand_data}.
    \item{}[event] \lstinline!PremiumPayDate!: Option premium payment date. \\
    Allowable values: See \lstinline!Date! in Table \ref{tab:allow_stand_data}.
    \item{}[number] \lstinline!PremiumAmount!: Option premium amount in \emph{PremiumPayCcy}. \\
    Allowable values: Any positive real number.
    \item{}[currency] \lstinline!PremiumCcy!: Option premium currency. \\
    Allowable values: See Table \ref{tab:currency} \lstinline!Currency!.
\end{itemize}
