%========================================================
\section{Netting Set Definitions}\label{sec:nettingsetinput}
%========================================================

The netting set definitions file - {\tt netting.xml} - 
contains a list of
definitions for various ISDA netting agreements. The file is written
in XML format. 

\vspace{1em}

Each netting set is defined within its own \lstinline!NettingSet!
node. All of these \lstinline!NettingSet! nodes are contained as
children of a \lstinline!NettingSetDefinitions! node.

\vspace{1em}

There are two distinct cases to consider:

\begin{itemize}
\item An ISDA agreement which does not contain a \emph{Credit Support
    Annex} (CSA).
\item An ISDA agreement which does contain a CSA.
\end{itemize}
%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection{Uncollateralised Netting Set}
%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
If an ISDA agreement does not contain a Credit Support Annex, the
portfolio exposures are not eligible for collateralisation. In such a
case the netting set can be defined within the following XML template:

\begin{listing}[H]
%\hrule\medskip
\begin{minted}[fontsize=\footnotesize]{xml}
    <NettingSet>
        <NettingSetId> </NettingSetId>
        <ActiveCSAFlag> </ActiveCSAFlag>
        <CSADetails></CSADetails>
    </NettingSet>
\end{minted}
\caption{Uncollateralised netting set definition}
\label{lst:nettingSetUncollat}
\end{listing}

The meanings of the various elements are as follows:
\begin{itemize}
\item \lstinline!NettingSetId!: The unique identifier for the ISDA netting set.
\ifdefined\RiskCatalogue{Alternatively, a \lstinline!NettingSetDetails!
node can be used, see Section \ref{sec:nettingsetdetails}.}\fi \\
Allowable values: Any string
\item \lstinline!ActiveCSAFlag! [Optional]: Boolean indicating whether the netting set is
  covered by a Credit Support Annex. 
  Allowable values: For uncollateralised netting sets
  this flag should be \emph{False}. If left blank or omitted, defaults to \emph{True}.
\item \lstinline!CSADetails! [Optional]: Node containing as children details of the governing
  Credit Support Annex. For uncollateralised netting sets, this node is not needed.
\end{itemize}
%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection{Collateralised Netting Set} \label{sec:CollNettingSet}
%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
If an ISDA agreement contains a Credit Support Annex, the
portfolio exposures are eligible for collateralisation. In such a
case the netting set can be defined within the following XML template:

\begin{listing}[H]
%\hrule\medskip
\begin{minted}[fontsize=\footnotesize]{xml}
    <NettingSet>
        <NettingSetId> </NettingSetId>
        <ActiveCSAFlag> </ActiveCSAFlag>
        <CSADetails>
            <Bilateral> </Bilateral>
            <CSACurrency> </CSACurrency>
            <Index> </Index>
            <ThresholdPay> </ThresholdPay>
            <ThresholdReceive> </ThresholdReceive>
            <MinimumTransferAmountPay> </MinimumTransferAmountPay>
            <MinimumTransferAmountReceive> </MinimumTransferAmountReceive>
            <IndependentAmount>
                <IndependentAmountHeld> </IndependentAmountHeld>
                <IndependentAmountType> </IndependentAmountType>
            </IndependentAmount>
            <MarginingFrequency>
                <CallFrequency> </CallFrequency>
                <PostFrequency> </PostFrequency>
            </MarginingFrequency>
            <MarginPeriodOfRisk> </MarginPeriodOfRisk>
            <CollateralCompoundingSpreadReceive> 
            </CollateralCompoundingSpreadReceive>
            <CollateralCompoundingSpreadPay> </CollateralCompoundingSpreadPay>
            <EligibleCollaterals>
                <Currencies>
                    <Currency>USD</Currency>
                    <Currency>EUR</Currency>
                    <Currency>CHF</Currency>
                    <Currency>GBP</Currency>
                    <Currency>JPY</Currency>
                    <Currency>AUD</Currency>
                </Currencies>
            </EligibleCollaterals>
            <ApplyInitialMargin>Y</ApplyInitialMargin>
            <InitialMarginType>Bilateral</InitialMarginType>
            <CalculateIMAmount>true</CalculateIMAmount>
            <CalculateVMAmount>true</CalculateVMAmount>
        </CSADetails>
    </NettingSet>
\end{minted}
\caption{Collateralised netting set definition}
\label{lst:nettingSetCollat}
\end{listing}

\subsubsection*{CSADetails}

The \lstinline!CSADetails! node contains details of the Credit Support
Annex which are relevant for the purposes of exposure calculation. The
meanings of the various elements are as follows:

\begin{itemize}
  \item \lstinline!Bilateral! [Optional]: There are three possible values here:
  \begin{itemize}
    \item \emph{Bilateral}: Both parties to the CSA are legally entitled to
      request collateral to cover their counterparty credit risk exposure
      on the underlying portfolio.
    \item \emph{CallOnly}: Only we are entitled to hold collateral; the
      counterparty has no such entitlement.
    \item \emph{PostOnly}: Only the counterparty is entitled to hold collateral;
      we have no such entitlement.
  \end{itemize}
  Defaults to \emph{Bilateral} if left blank or omitted.
  
  \item \lstinline!CSACurrency! [Optional]: A three-letter ISO code specifying the master
  currency of the CSA. All monetary values specified within the CSA are
  assumed to be denominated in this currency.\\
  Allowable values: Any currency. See Table \ref{tab:currency}.

  \item \lstinline!Index! [Optional]: The index is used to derive the fixing which is used
  for compounding cash collateral in the master currency of the CSA.\\
  Allowable values: An alphanumeric string of the form CCY-INDEX-TENOR. CCY, INDEX and TENOR must be separated by dashes (-). CCY and INDEX must be among the supported currency and index combinations. TENOR must be an integer followed by \emph{D}, \emph{W}, \emph{M} or \emph{Y}, except for Overnight indices which do not require a TENOR. See Table \ref{tab:indices}.

  \item \lstinline!ThresholdPay! [Optional]: A threshold amount above which the
  counterparty is entitled to request collateral to cover excess
  exposure.\\
  Allowable values: Any number.

  \item \lstinline!ThresholdReceive! [Optional]: A threshold amount above which we are
  entitled to request collateral from the counterparty to cover excess
  exposure.\\
  Allowable values: Any number.

  \item \lstinline!MinimumTransferAmountPay! [Optional]: Any margin calls issued by the
  counterparty must exceed this minimum transfer amount. If the
  collateral shortfall is less than this amount, the counterparty is not
  entitled to request margin.\\
  Allowable values: Any number.

  \item \lstinline!MinimumTransferAmountReceive! [Optional]: Any margin calls issued by us
  to the counterparty must exceed this minimum transfer amount. If the
  collateral shortfall is less than this amount, we are  not
  entitled to request margin.\\
  Allowable values: Any number.

  \item \lstinline!IndependentAmount! [Optional]: This element contains two child nodes:
    \begin{itemize}
      \item \lstinline!IndependentAmountHeld!: The netted sum of all independent amounts
        covered by this ISDA agreement/CSA. \\
        Allowable values: Any number. A negative number implies that the counterparty
        holds the independent amount.
      \item \lstinline!IndependentAmountType!: The nature of the independent amount as
        defined within the Credit Support Annex. \\
        Allowable values: The only supported value here is \emph{FIXED}.
    \end{itemize}

  \item \lstinline!MarginingFrequency!: This element contains two child nodes:
  \begin{itemize}
    \item \lstinline!CallFrequency!: The frequency with which we are entitled to
      request additional margin from the counterparty (e.g. \emph{1D},
      \emph{2W}, \emph{1M}). \\
      Allowable values: 
    \item \lstinline!PostFrequency!: The frequency with which the counterparty is entitled to
      request additional margin from us. \\
      Allowable values: Any period definition (e.g.\ \emph{2D}, \emph{1W}, \emph{1M},
      \emph{1Y}).
  \end{itemize}
  This covers only the case where only one party has to post an
  independent amount. In a future release this will be extended to the
  situation prescribed by the Basel/IOSCO regulation (initial margin to
  be posted by both parties without netting).

  \item \lstinline!MarginPeriodOfRisk!: The length of time assumed necessary
  for closing out the portfolio position after a default event. \\
    Allowable values: Any period definition (e.g.\ \emph{2D}, \emph{1W}, \emph{1M},
      \emph{1Y}).

  \item \lstinline!CollateralCompoundingSpreadReceive!: The spread over the O/N
  interest accrual rate taken by the clearing house, when holding
  collateral. \\
  Allowable values: Any number.

  \item \lstinline!CollateralCompoundingSpreadPay!: The spread over the O/N
  interest accrual rate taken by the clearing house, when collateral is
  held by the counterparty. \\
  Allowable values: Any number.

  \item \lstinline!EligibleCollaterals!: For now the only supported type of
  collateral is cash. If the CSA specifies a set of currencies which
  are eligible as collateral, these can be listed using
  \lstinline!Currency! nodes. \\
  Allowable values: Any currency. See Table \ref{tab:currency}.

  \item \lstinline!ApplyInitialMargin!: Apply (dynamic) initial Margin in
  addition to variation margin \\
  Allowable values: Boolean node, the set of allowable values is given in
  Table \ref{tab:boolean_allowable}.

  \item \lstinline!InitialMarginType! There are three possible values here:
  \begin{itemize}
    \item \emph{Bilateral}: Both parties to the CSA are legally entitled to
      request collateral to cover their MPOR risk exposure
      on the underlying portfolio.
    \item \emph{CallOnly}: Only we are entitled to hold collateral; the
      counterparty has no such entitlement.
    \item \emph{PostOnly}: Only the counterparty is entitled to hold collateral;
      we have no such entitlement.
  \end{itemize}

  \item \lstinline!CalculateIMAmount!: Boolean indicating whether to calculate
    initial margin from SIMM. For uncollateralised netting sets
    this flag will be ignored. This only applies to the SA-CCR
    calculations. \\
    Allowable values: Boolean node, the set of allowable values is given in
    Table \ref{tab:boolean_allowable}.

  \item \lstinline!CalculateVMAmount!: Boolean indicating whether to calculate
    variation margin from the netting set NPV. For uncollateralised netting
    sets this flag will be ignored. This only applies to the SA-CCR
    calculations. \\
    Allowable values: Boolean node, the set of allowable values is given in
    Table \ref{tab:boolean_allowable}.
\end{itemize}
