%========================================================
\section{Trade Data}\label{sec:portfolio_data}
%========================================================

The trades that make up the portfolio are specified in an XML file where the portfolio data is specified in a hierarchy
of nodes and sub-nodes.  The nodes containing individual trade data are referred to as elements or XML elements. These
are generally the lowest level nodes.

\vspace{1em}

The top level portfolio node is delimited by an opening {\tt <Portfolio>} and a closing {\tt </Portfolio>} tag. Within
the portfolio node, each trade is defined by a starting {\tt <Trade id="[Tradeid]">} and a closing {\tt </Trade>} tag.
Further, the trade type is set by the TradeType XML element. Each trade has an Envelope node that includes the same XML
elements for all trade types (Id, Type, Counterparty, Rating, NettingSetId) plus the Additional fields node, and after
that, a node containing trade specific data.

\vspace{1em}
An example of a {\tt portfolio.xml} file with one Swap trade including the full envelope node is shown in Listing \ref{lst:portfolio}.

\begin{listing}[H]
%\hrule\medskip
\begin{minted}[fontsize=\footnotesize]{xml}
<Portfolio>
  <Trade id="Swap#1">
    <TradeType> Swap </TradeType>
    <Envelope>
      <CounterParty> Counterparty#1 </CounterParty>
      <NettingSetId> NettingSet#2 </NettingSetId>
      <PortfolioIds>
          <PortoliodId> PF#1 </PortfolioId>
          <PortoliodId> PF#2 </PortfolioId>
      </PortfolioIds>
      <AdditionalFields>
        <Sector> SectorA </Sector>
        <Book> BookB </Book>
        <Rating> A1 </Rating>
      </AdditionalFields>
    </Envelope>
    <SwapData>
        ...
        [Trade specific data for a Swap]
        ...
    </SwapData>
  </Trade>
</Portfolio>
\end{minted}
\caption{Portfolio}
\label{lst:portfolio}
\end{listing}

A description of all portfolio data, i.e. of each node and XML element in the portfolio file, with examples and
allowable values follows below. There are two XML elements directly under the top level {\tt Portfolio} node:

\begin{itemize}
\item {\tt Trade id}: The first element of each trade is the {\tt Trade id} and it is used to identify trades within a
  portfolio. Trade ids should be unique within a portfolio.  The {\tt
    Trade id} element is entered as an attribute to the XML element {\tt <Trade>}, such as {\tt <Trade id="ExampleTrade">}
  in the beginning closed by {\tt </Trade>} at the end of the trade data.

Allowable values:  Any alphanumeric string. The underscore (\_) sign may be used as well. 


\item {\tt TradeType}: %The Trade type is set with the {\tt TradeType} element, as well as with the {\tt Type} element in  the envelope. The two Trade type entries should be identical. 
ORE currently supports 14 trade types.

%Allowable values:  \emph{Swap, CapFloor, Swaption, FxForward, FxOption, Bond, CreditDefaultSwap}
Allowable values: \emph{ForwardRateAgreement, Swap, CapFloor, Swaption, FxForward, FxSwap, FxOption,
EquityForward, EquityOption, VarianceSwap, CommodityForward, CommodityOption, CreditDefaultSwap, Bond}

\end{itemize}

%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection{Envelope}\label{ss:envelope}
%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
The envelope node contains basic identifying details of a trade ({\tt
  Id}, {\tt Type}, {\tt Counterparty}, {\tt NettingSetId}), a 
{\tt PortfolioIds} node containing a list of portfolio assignments, 
plus an {\tt AdditionalFields} node where custom
elements can be added for informational purposes such as {\tt Book} or
{\tt Sector}. Beside the custom elements within the {\tt
  AdditionalFields} node, the envelope contains the same elements for
all Trade types.  The {\tt Id}, {\tt Type}, {\tt Counterparty} and
{\tt NettingSetId} elements must have non-blank entries for ORE to
run. 
%, whereas ORE will run without a {\tt Rating} element but fail to produce a CVA. \\
The meanings and allowable values of the various elements in the \lstinline!Envelope!  node follow below.

\begin{itemize}
\item {\tt Id}: The {\tt Id} element in the envelope is used to identify trades within a portfolio. It should be set to
  identical values as the {\tt Trade id=" "} element.

  Allowable values: Any alphanumeric string. The underscore (\_) sign may be used as well.

%\item {\tt Type}: The Trade Type is in addition to being set in the {\tt ClassName} element, also set by the {\tt Type}
%  element in the envelope. Both elements should have the same entry.
%
%Allowable values: \emph{ForwardRateAgreement, Swap, CapFloor, Swaption, FxForward, FxSwap, FxOption,
%EquityForward, EquityOption, CreditDefaultSwap, Bond}

\item {\tt Counterparty}: Specifies the name of the counterparty of the trade.  It is used to show exposure analytics by
  counterparty.

Allowable values: Any alphanumeric string. Underscores (\_) and blank spaces may be used as well. 

%\item {\tt Rating} [Optional]: The {\tt Rating} element specifies the default curve that will be used in the CVA
% calculations.  No CVA will be calculated if omitted or left blank.

%Allowable values: An alphanumeric string that matches default curve names in the market configuration file.  

\item {\tt NettingSetId} [Optional]: The {\tt NettingSetId} element specifies the identifier for a netting set. If a
  \lstinline!NettingSetId! is specified, the trade is eligible for close-out netting under the terms of an associated
  ISDA agreement. The specified {\tt NettingSetId} must be defined within the netting set definitions file
  (see section \ref{sec:nettingsetinput}). If left blank or omitted the trade will not belong to any netting set, and thus not be
  eligible for netting.

Allowable values: Any alphanumeric string. Underscores (\_) and blank spaces may be used as well. 

% -- specified netting --Negative transaction values offset exposures from positive transaction values within specified
% netting groups. Total netting
% group %-- exposures and exposures from transactions not belonging to a netting group are then combined without offsetting.

\item \lstinline!PortfolioIds! [Optional]: The PortfolioIds node
  allows the assignment of a given trade to several portfolios, each
  enclosed in its own pair of tags {\tt <PortfolioId>} and {\tt
    </PortfolioId>} . Note that ORE does not assume a hierarchical 
 organisation of such portfolios. If present, the portfolio IDs will be used in the
  generation of some ORE reports such as the VaR report which provides
  breakdown by any portfolio id that occurs in the trades' envelopes.

Allowable values for each PortfolioId: Any string.

\item \lstinline!AdditionalFields! [Optional]: The AdditionalFields node allows the insertion of additional trade
  information using custom XML elements.  For example, elements such as Sector, Desk or Folder can be used. The elements
  within the \lstinline!AdditionalFields! node are used for
  informational purposes only, and do not affect any analytics in ORE.

Allowable values: Any custom element.

\end{itemize}

%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection{Trade Specific Data}
%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -

After the envelope node, trade-specific data for each trade type supported by
ORE is included. 
Each trade type has its own trade data container which is defined by an XML node containing a trade-specific
configuration of individual XML tags - called elements - and trade components. The trade components are defined by XML
sub-nodes that can be used within multiple trade data containers, i.e.  by multiple trade types.

\vspace{1em}

Details of  trade-specific data for all trade types follow below.

\subsubsection{Swap}

The \lstinline!SwapData! node is the trade data container for the Swap trade type. A Swap must have at least one leg,
and can have an unlimited number of legs. Each leg is represented by a \lstinline!LegData! trade component sub-node,
described in section \ref{ss:leg_data}. An example structure of a two-legged \lstinline!SwapData!
node is shown in Listing \ref{lst:swap_data}.

\begin{listing}[H]
%\hrule\medskip
\begin{minted}[fontsize=\footnotesize]{xml}
<SwapData>
  <LegData>
    ...
  </LegData>
  <LegData>
    ...
  </LegData>
</SwapData>
\end{minted}
\caption{Swap data}
\label{lst:swap_data}
\end{listing}

\subsubsection{Cap/Floor}

The \lstinline!CapFloorData! node is the trade data container for trade type CapFloors.  It's a cap, floor or collar
(i.e. a portfolio of a long cap and a short floor for a long position in the collar) on a series of Ibor or CMS rates. The
\lstinline!CapFloorData! node contains a \lstinline!LongShort! sub-node which indicates whether the cap (floor, collar)
is long or short, and a \lstinline!LegData!  sub-node where the LegType element must be set to \emph{Floating} or \emph{CMS}, plus
elements for the Cap and Floor rates. An example structure with Cap rates is shown in in Listing
\ref{lst:capfloor_data}. A \lstinline!CapFloorData! node must have either \lstinline!Caps! or \lstinline!Floors!
elements, or both.

\begin{listing}[H]
%\hrule\medskip
\begin{minted}[fontsize=\footnotesize]{xml}
  <CapFloorData>
  <LongShort>Long</LongShort>
  <LegData>
    <Payer>false</Payer>
    <LegType>Floating</LegType>
     ...
  </LegData>
  <Caps>
    <Rate>0.05</Rate>
  </Caps>
</CapFloorData>
\end{minted}
\caption{Cap/Floor data}
\label{lst:capfloor_data}
\end{listing}

The meanings and allowable values of the elements in the \lstinline!CapFloorData!  node follow below.

\begin{itemize}

\item LongShort: This node defines the position in the cap (floor, collar) and can take values \lstinline!Long! or
  \lstinline!Short!

\item LegData: This is a trade component sub-node outlined in section \ref{ss:leg_data}. Exactly
  one \lstinline!LegData! node is allowed and the LegType element must be set to \emph{Floating} or \emph{CMS}.

\item Caps: This node has child elements of type \lstinline!Rate!
  capping the floating leg. The first rate value corresponds to the
  first coupon, the second rate value corresponds to the second
  coupon, etc. If the number of coupons exceeds the number of rate
  values, the rate will be kept flat at the value of last entered rate
  for the remaining coupons. For a fixed cap rate over all coupons,
  one single rate value is sufficient. The number of entered rate
  values cannot exceed the number of coupons. 

  Allowable values for each \lstinline!Rate! element: Any real number. The rate is expressed in decimal form, eg 0.05 is
  a rate of 5\%

\item Floors: This node has child elements of type
  \lstinline!Rate! flooring the floating leg.  The first rate value
  corresponds to the first coupon, the second rate value corresponds
  to the second coupon, etc. If the number of coupons exceeds the
  number of rate values, the rate will be kept flat at the value of
  last entered rate for the remaining coupons. For a fixed floor rate
  over all coupons, one single rate value is sufficient. The number of
  entered rate values cannot exceed the number of coupons.

  Allowable values for each \lstinline!Rate! element: Any real number. The rate is expressed in decimal form, eg 0.05 is
  a rate of 5\%

\end{itemize}

\subsubsection{Swaption}

The \lstinline!SwaptionData!  node is the trade data container for the Swaption trade type. The \lstinline!SwaptionData!
node has one and exactly one \lstinline!OptionData! trade component sub-node, and at least one \lstinline!LegData! trade
component sub-node.  These trade components are outlined in section \ref{ss:option_data} and section
\ref{ss:leg_data}.\\

Supported swaption exercise styles are European and Bermudan. European swaptions can have unlimited number of legs, with
each leg represented by a \lstinline!LegData! sub-node. Bermudan swaptions must have two legs, i.e. two
\lstinline!LegData! sub-nodes. See Table \ref{tab:bermudan_requirements} for further details on requirements for
Bermudan swaptions. Cross currency swaptions are not supported for either exercise style, i.e. the Currency element must
have the same value for all \lstinline!LegData! sub-nodes of a swaption.\\

The structure of an example \lstinline!SwaptionData!  node of a two-legged European swaption is shown in Listing
\ref{lst:swaption_data}.

\begin{listing}[H]
%\hrule\medskip
\begin{minted}[fontsize=\footnotesize]{xml}
<SwaptionData>
    <OptionData>
        <Style>European</Style>
        ...
    </OptionData>
    <LegData>
        <Currency>GBP</Currency>
        ...
    </LegData>
    <LegData>
        <Currency>GBP</Currency>
        ...
    </LegData>
</SwaptionData>
\end{minted}
\caption{Swaption data}
\label{lst:swaption_data}
\end{listing}

\begin{table}[H]
\centering
\begin{tabu} to 0.9\linewidth {| X[-1.5,l,m] | X[-5,l,m] |}
    \hline
        & \bfseries{A Bermudan Swaption requires:} \\  \hline
    \lstinline!OptionData! & One \lstinline!OptionData! sub-node  \\  \hline
   \lstinline!Style! &  \emph{Bermudan}\\ \hline
    \lstinline!ExerciseDates! & At least two \lstinline!ExerciseDate! child elements.\\ \hline
    \lstinline!LegData! &  Two \lstinline!LegData! sub-nodes \\ \hline
    \lstinline!LegType! & \emph{Fixed} on one node and \emph{Floating} on the other.\\ \hline    
    \lstinline!Currency! & The same currency for both nodes.\\ \hline 
%    \lstinline!Notionals! & No accretion or amortisation, just a constant notional. Exactly one \lstinline!Notional! child element for each node.\\ \hline
%   \lstinline!Rates! & A constant rate. The fixed rate node should have exactly one \lstinline!Rate! child element.\\ \hline
%    \lstinline!Spreads! &  A constant spread. The floating rate node should have exactly one \lstinline!Spread! child element.\\ \hline
%    \bfseries{ScheduleData} &   \\ \hline   
%    \lstinline!IsRuleBased! & Must be \emph{true} for both nodes. TBC: Fixed by Henning?\\ \hline      
  \end{tabu}
  \caption{Requirements for Bermudan Swaptions}
  \label{tab:bermudan_requirements}
\end{table}

\subsubsection{FX Forward}

The \lstinline!FXForwardData!  node is the trade data container for the FX Forward trade type.  The structure -
including example values - of the \lstinline!FXForwardData!  node is shown in Listing \ref{lst:fxforward_data}. It
contains no sub-nodes.

\begin{listing}[H]
%\hrule\medskip
\begin{minted}[fontsize=\footnotesize]{xml}
        <FxForwardData>
            <ValueDate>2023-04-09</ValueDate>
            <BoughtCurrency>EUR</BoughtCurrency>
            <BoughtAmount>1000000</BoughtAmount>
            <SoldCurrency>USD</SoldCurrency>
            <SoldAmount>1500000</SoldAmount>
        </FxForwardData>
\end{minted}
\caption{FX Forward data}
\label{lst:fxforward_data}
\end{listing}

The meanings and allowable values of the various elements in the \lstinline!FXForwardData!  node follow below.  All elements are required.

\begin{itemize}
\item ValueDate: The value date of the FX Forward. \\ Allowable values:  See \lstinline!Date! in Table \ref{tab:allow_stand_data}.
\item BoughtCurrency: The currency to be bought on value date.  \\ Allowable values:  See \lstinline!Currency! in Table \ref{tab:allow_stand_data}.
\item BoughtAmount: The amount to be bought on value date.  \\ Allowable values:  Any positive real number.
\item SoldCurrency: The currency to be sold on value date.  \\ Allowable values:  See \lstinline!Currency! in Table \ref{tab:allow_stand_data}.
\item SoldAmount: The amount to be sold on value date.  \\ Allowable values:  Any positive real number.

\end{itemize}

\subsubsection{FX Swap}

The \lstinline!FXSwapData!  node is the trade data container for the FX Swap trade type.  The structure -
including example values - of the \lstinline!FXSwapData!  node is shown in Listing 
\ref{lst:fxswap_data}. 
It contains no sub-nodes.

\begin{listing}[H]
%\hrule\medskip
\begin{minted}[fontsize=\footnotesize]{xml}
        <FxSwapData>
            <NearDate>2018-09-01</NearDate>
            <NearBoughtCurrency>EUR</NearBoughtCurrency>
            <NearBoughtAmount>1000000</NearBoughtAmount>
            <NearSoldCurrency>USD</NearSoldCurrency>
            <NearSoldAmount>1140000</NearSoldAmount>
             <FarDate>2028-09-01</FarDate>
            <FarBoughtAmount>1300000</FarBoughtAmount>
            <FarSoldAmount>1000000</FarSoldAmount>
        </FxSwapData>
\end{minted}
\caption{FX Swap data}
\label{lst:fxswap_data}
\end{listing}

The meanings and allowable values of the various elements in the \lstinline!FXSwapData!  node follow below.  All elements are required.

\begin{itemize}
\item NearDate: The date of the initial fx exchange of the FX Swap. \\ Allowable values:  See \lstinline!Date! in Table \ref{tab:allow_stand_data}.
\item NearBoughtCurrency: The currency to be bought in the initial exchange at near date, and sold in the final exchange at far date.  \\ Allowable values:  See \lstinline!Currency! in Table \ref{tab:allow_stand_data}.
\item NearBoughtAmount: The amount to be bought on near date.  \\ Allowable values:  Any positive real number.
\item NearSoldCurrency: The currency to be sold in the initial fx exchange at near date, and bought in the final exchange at far date.   \\ Allowable values:  See \lstinline!Currency! in Table \ref{tab:allow_stand_data}.
\item NearSoldAmount: The amount to be sold on near date.  \\ Allowable values:  Any positive real number.
\item FarDate: The date of the final fx exchange of the FX Swap. \\ Allowable values:  Any date further into the future than NearDate. See \lstinline!Date! in Table  \ref{tab:allow_stand_data}.
\item FarBoughtAmount: The amount to be bought on far date.  \\ Allowable values:  Any positive real number.
\item FarSoldAmount: The amount to be sold on far date.  \\ Allowable values:  Any positive real number.
\end{itemize}

\subsubsection{FX Option}

The \lstinline!FXOptionData!  node is the trade data container for the FX Option trade type.  Vanilla FX options are
supported, the exercise style must be \emph{European}. The strike rate of an FX option is: SoldAmount / BoughtAmount. The
\lstinline!FXOptionData!  node includes one and only one \lstinline!OptionData! trade component sub-node plus elements
specific to the FX Option. The structure of an example \lstinline!FXOptionData! node for a FX Option is shown in Listing
\ref{lst:fxoption_data}.

\begin{listing}[H]
%\hrule\medskip
\begin{minted}[fontsize=\footnotesize]{xml}
        <FxOptionData>
            <OptionData>
             ...
            </OptionData>
            <BoughtCurrency>EUR</BoughtCurrency>
            <BoughtAmount>1000000</BoughtAmount>
            <SoldCurrency>USD</SoldCurrency>
            <SoldAmount>1350000</SoldAmount>
        </FxOptionData>
\end{minted}
\caption{FX Option data}
\label{lst:fxoption_data}
\end{listing}

The meanings and allowable values of the elements in the \lstinline!FXOptionData!  node follow below.

\begin{itemize}
\item OptionData: This is a trade component sub-node outlined in section \ref{ss:option_data}. Note that the
  FX option type allows for \emph{European} option style only.

\item BoughtCurrency: The bought currency of the FX option.  

Allowable values:  See Currency in Table \ref{tab:allow_stand_data}.

\item BoughtAmount: The amount in the BoughtCurrency.  

Allowable values:  Any positive real number.

\item SoldCurrency: The sold currency of the FX option.  

Allowable values:  See Currency in Table \ref{tab:allow_stand_data}.

\item SoldAmount: The amount in the SoldCurrency.  

Allowable values:  Any positive real number.

\end{itemize}



\subsubsection{Equity Option}

The \lstinline!EquityOptionData!  node is the trade data container for the equity option trade type.  Vanilla equity 
options are supported, the exercise style must be \emph{European}. The \lstinline!EquityOptionData!  node includes one and 
only one \lstinline!OptionData! trade component sub-node plus elements specific to the equity option. The structure of 
an example \lstinline!EquityOptionData! node for an equity option is shown in Listing
\ref{lst:eqoption_data}.

\begin{listing}[H]
%\hrule\medskip
\begin{minted}[fontsize=\footnotesize]{xml}
<EquityOptionData>
    <OptionData>
      ...
    </OptionData>
    <Name>SP5</Name>
    <Currency>USD</Currency>
    <Strike>2147.56</Strike>
    <Quantity>17000</Quantity>
</EquityOptionData>
\end{minted}
\caption{Equity Option data}
\label{lst:eqoption_data}
\end{listing}

The meanings and allowable values of the elements in the \lstinline!EquityOptionData!  node follow below.

\begin{itemize}
	\item OptionData: This is a trade component sub-node outlined in section \ref{ss:option_data} Option Data. Note 
	that the equity option type allows for \emph{European} option style only.	
	\item Name: The name of the underlying equity. \\
	Allowable values:  Any string (provided it is the ID of an equity in the market configuration).
	\item Currency: The currency of the equity option. \\
	Allowable values:  See Currency in Table \ref{tab:allow_stand_data}.	
	\item Strike: The option strike price.\\
	Allowable values:  Any positive real number.	
	\item Quantity: The number of units of the underlying covered by the transaction. \\
	Allowable values:  Any positive real number.
\end{itemize}

\subsubsection{Equity Forward}

The \lstinline!EquityForwardData!  node is the trade data container for the equity forward trade type.  Vanilla equity 
forwards are supported. The structure of an example \lstinline!EquityForwardData! node for an equity option is shown in 
Listing \ref{lst:eqfwd_data}.

\begin{listing}[H]
%\hrule\medskip
\begin{minted}[fontsize=\footnotesize]{xml}
<EquityForwardData>
  <LongShort>Long</LongShort>
  <Maturity>2018-06-30</Maturity>
  <Name>SP5</Name>
  <Currency>USD</Currency>
  <Strike>2147.56</Strike>
  <Quantity>17000</Quantity>
</EquityForwardData>
\end{minted}
\caption{Equity Forward data}
\label{lst:eqfwd_data}
\end{listing}

The meanings and allowable values of the elements in the \lstinline!EquityForwardData!  node follow below.

\begin{itemize}
	\item LongShort: Defines whether the underlying equity will be bought (long) or sold (short). \\
	Allowable values: Long, Short.
	\item Maturity: The maturity date of the forward contract, i.e. the date when the underlying equity will be bought/sold. \\
	Allowable values: Any date string.
	\item Name: The name of the underlying equity or equity index. \\
	Allowable values:  Any string (provided it is the ID of an equity in the market configuration).
	\item Currency: The  currency of the equity forward. \\
	Allowable values:  See Currency in Table \ref{tab:allow_stand_data}.	
	\item Strike: The agreed buy/sell price of the equity forward. \\
	Allowable values:  Any positive real number.	
	\item Quantity: The number of units of the underlying equity to be bought/sold. \\
	Allowable values:  Any positive real number.
\end{itemize}

\subsubsection{Variance Swap}

The \lstinline!VarianceSwapData!  node is the trade data container for the variance swap trade type. Only vanilla variance swaps are supported, and only pricing. The structure of an example \lstinline!VarianceSwapData! node for an equity option is shown in Listing \ref{lst:varswap_data}. It should be noted that a variance swap starting today or before today requires fixings to be provided for all business days (according to the calendar provided) from the day before the start date up to the most recent business day.

\begin{listing}[H]
	%\hrule\medskip
	\begin{minted}[fontsize=\footnotesize]{xml}
<VarianceSwapData>
  <Name>SP5</Name>
  <Currency>USD</Currency>
  <StartDate>2016-01-29</StartDate>
  <EndDate>2016-07-29</EndDate>
  <Calendar>US</Calendar>
  <Strike>0.2</Strike>
  <Notional>50000</Notional>
  <LongShort>Long<LongShort>
</VarianceSwapData>
	\end{minted}
	\caption{Variance Swap data}
	\label{lst:varswap_data}
\end{listing}

The meanings and allowable values of the elements in the \lstinline!VarianceSwapData!  node below.

\begin{itemize}
	\item Name: The name of the underlying equity. \\
	Allowable values:  Any string (provided it is the ID of an equity in the market configuration).
	\item Currency: The bought currency of the variance swap. \\
	Allowable values:  See \lstinline!Currency! in Table \ref{tab:allow_stand_data}.	
	\item StartDate: The variance swap start date. \\
	Allowable values:  See \lstinline!Date! in Table \ref{tab:allow_stand_data}.	
	\item EndDate: The variance swap end date. \\
	Allowable values:  See \lstinline!Date! in Table \ref{tab:allow_stand_data}.	
	\item Calendar: The calendar according to which variance is accrued. \\
	Allowable values: See Table \ref{tab:calendar}.
	\item Strike: The volatility strike of the variance swap quoted absolutely (i.e. not as a percent). If the swap was struck in terms of variance, the square root of that variance should be used here.\\
	Allowable values:  Any positive real number.
	\item Notional: The vega notional of the variance swap. This is the notional in terms of volatility units (like the strike). If the swap was struck in terms of a variance notional, the corresponding vega notional is given by $N_{vol} = N_{var} * 2 * 100 * K_{vol}$ (where $K_{vol}$ is in absolute terms).\\
	Allowable values:  Any positive real number.
	\item LongShort: Defines whether the trade is long in the equity variance. For the avoidance of doubt, a long variance swap has positive value if the realised variance exceeds the variance strike. \\
	Allowable values: Long, Short.
\end{itemize}

\subsubsection{CPI Swap}

A CPI swap is set up as a swap, with one leg of type {\tt CPI}. Listing \ref{lst:cpiswap} shows an example. The
CPI leg contains an additional {\tt CPILegData} block. See \ref{ss:cpilegdata} for details on the CPI leg specification.

\begin{listing}[H]
%\hrule\medskip
\begin{minted}[fontsize=\footnotesize]{xml}
    <SwapData>
      <LegData>
        <LegType>Floating</LegType>
        <Payer>true</Payer>
        ...
      </LegData>
      <LegData>
        <LegType>CPI</LegType>
        <Payer>false</Payer>
        ...
        <CPILegData>
        ...
        </CPILegData>
      </LegData>
    </SwapData>
\end{minted}
\caption{CPI Swap Data}
\label{lst:cpiswap}
\end{listing}

\subsubsection{Year on Year Inflation Swap}

A Year on Year inflation swap is set up as a swap, with one leg of type {\tt YY}. Listing \ref{lst:yyswap} shows an
example. The YY leg contains an additional {\tt YYLegData} block. See \ref{ss:yylegdata} for details on the YY leg
specification.

\begin{listing}[H]
%\hrule\medskip
\begin{minted}[fontsize=\footnotesize]{xml}
    <SwapData>
      <LegData>
        <LegType>Floating</LegType>
        <Payer>true</Payer>
        ...
      </LegData>
      <LegData>
        <LegType>YY</LegType>
        <Payer>false</Payer>
        ...
        <YYLegData>
        ...
        </YYLegData>
      </LegData>
    </SwapData>
\end{minted}
\caption{Year on Year Swap Data}
\label{lst:yyswap}
\end{listing}

\subsubsection{Bond}

A vanilla Bond is set up using a {\tt BondData} block as shown in listing \ref{lst:bonddata}. The bond specific elements
are

\begin{itemize}
\item IssuerId: A unique identifier for the issuer of the bond
\item CreditCurveId: The entity defining the default curve used for pricing, via the default curves block in {\tt
    todaysmarket.xml}
% \item LGD (optional): If given, this LGD is used for pricing, overriding the default LGD of the default curve
\item SecurityId: A unique identifier for the security, this defines the security specific spread to be used for
  pricing.
\item ReferenceCurveId: The benchmark curve to be used for pricing, this must match a name of a curve in the yield
  curves block in {\tt todaysmarket.xml}.
\item SettlementDays: The settlement delay applicable to the security.
\item Calendar: The calendar associated to the settlement lag.
\item IssueDate: The issue date of the security.
\end{itemize}

A LegData block then defines the cashflow structure of the bond, this can be of type fixed, floating etc.

\begin{listing}[H]
%\hrule\medskip
\begin{minted}[fontsize=\footnotesize]{xml}
    <BondData>
        <IssuerId>CPTY_C</IssuerId>
        <CreditCurveId>CPTY_C</CreditCurveId>
        <SecurityId>SECURITY_1</SecurityId>
        <ReferenceCurveId>EUR-EURIBOR-6M</ReferenceCurveId>
        <SettlementDays>2</SettlementDays>
        <Calendar>TARGET</Calendar>
        <IssueDate>20160203</IssueDate>
        <LegData>
            <LegType>Fixed</LegType>
            <Payer>false</Payer>
            ...
        </LegData>
    </BondData>
\end{minted}
\caption{Bond Data}
\label{lst:bonddata}
\end{listing}

The bond pricing requires a recovery rate that can be specified in ORE per SecurityId, see sections \ref{sec:curveconfig} and \ref{md:sec_rec_rates}. 

\subsubsection{Credit Default Swap}

A credit default swap is set up using a {\tt CreditDefaultSwapData} block as shown in listing \ref{lst:cdsdata}. The CDS specific elements
are

\begin{itemize}
\item IssuerId: A unique identifier for the issuer of the bond
\item CreditCurveId: The entity defining the default curve used for pricing, via the default curves block in {\tt
    todaysmarket.xml}
\item SettlesAccrual: Whether or not the accrued coupon is due in the event of a default.
\item PaysAtDefaultTime: If set to true, any payments triggered by a default event are due at default time. If set to false, they are due at the end of the accrual period.
\item ProtectionStart: The first date where a default event will trigger the contract.
\item UpfrontDate: Settlement date for the upfront payment.
\item UpfrontFee: The upfront payment, expressed as a rate, to be multiplied by notional amount.
\end{itemize}

A LegData block then defines the cashflow structure of the credit default swap, this must be be of type fixed.

\begin{listing}[H]
%\hrule\medskip
\begin{minted}[fontsize=\footnotesize]{xml}
    <CreditDefaultSwapData>
      <IssuerId>CPTY_A</IssuerId>
      <CreditCurveId>BANK</CreditCurveId>
      <SettlesAccrual>Y</SettlesAccrual>
      <PaysAtDefaultTime>Y</PaysAtDefaultTime>
      <ProtectionStart>20160206</ProtectionStart>
      <UpfrontDate>20160208</UpfrontDate>
      <UpfrontFee>0.0</UpfrontFee>
      <LegData>
            <LegType>Fixed</LegType>
            <Payer>false</Payer>
            ...
        </LegData>
    </CreditDefaultSwapData>
\end{minted}
\caption{CreditDefaultSwap Data}
\label{lst:cdsdata}
\end{listing}

\subsubsection{Forward Rate Agreement}

A forward rate agreement is set up using a {\tt ForwardRateAgreementData} block as shown in listing \ref{lst:ForwardRateAgreementdata}. The forward rate agreement specific elements
are

\begin{itemize}
\item StartDate: A FRA expires/settles on the startDate. \\
Allowable values:  See \lstinline!Date! in Table \ref{tab:allow_stand_data}.

\item EndDate: EndDate is the date when the forward loan or deposit ends. It follows that (EndDate - StartDate) is the tenor/term of the underlying loan or deposit.
\item Currency: The currency of the FRA notional. \\
Allowable values:  See Currency in Table \ref{tab:allow_stand_data}.	
\item Index: The name of the interest rate index the FRA is benchmarked against.
\item LongShort: Specifies whether the FRA position is long (one receives the agreed rate) or short (one pays the agreed rate).
\item Strike: The agreed forward interest rate.
\item Notional: No accretion or amortisation, just a constant notional.
\end{itemize}

A LegData block then defines the cashflow structure of the bond, this can be of type fixed, floating etc.

\begin{listing}[H]
%\hrule\medskip
\begin{minted}[fontsize=\footnotesize]{xml}
    <ForwardRateAgreementData>
        <StartDate>20161028</StartDate>
        <EndDate>20351028</EndDate>
        <Currency>EUR</Currency>
        <Index>EUR-EURIBOR-6M</Index>
        <LongShort>Long</LongShort>
        <Strike>0.00001</Strike>
        <Notional>1000000000</Notional>
    </ForwardRateAgreementData>
\end{minted}
\caption{Forward Rate Agreement Data}
\label{lst:ForwardRateAgreementdata}
\end{listing}


\subsubsection{Commodity Option}

The \lstinline!CommodityOptionData!  node is the trade data container for the commodity option trade type.  Vanilla commodity 
options are supported, the exercise style must be \emph{European}. The \lstinline!CommodityOptionData!  node includes one and 
only one \lstinline!OptionData! trade component sub-node plus elements specific to the commodity option. The structure of 
an example \lstinline!CommodityOptionData! node for a commodity option is shown in Listing
\ref{lst:comoption_data}.

\begin{listing}[H]
%\hrule\medskip
\begin{minted}[fontsize=\footnotesize]{xml}
<CommodityOptionData>
    <OptionData>
      ...
    </OptionData>
    <Name>COMDTY_WTI_USD</Name>
    <Currency>USD</Currency>
    <Strike>70</Strike>
    <Quantity>500000</Quantity>
</CommodityOptionData>
\end{minted}
\caption{Commodity Option data}
\label{lst:comoption_data}
\end{listing}

The meanings and allowable values of the elements in the \lstinline!CommodityOptionData!  node follow below.

\begin{itemize}
	\item OptionData: This is a trade component sub-node outlined in section \ref{ss:option_data} Option Data. Note 
	that the commodity option type allows for \emph{European} option style only.	
	\item Name: The name of the underlying commodity. \\
	Allowable values:  Any string (provided it is the ID of a commodity in the market configuration).
	\item Currency: The currency of the commodity option. \\
	Allowable values:  See Currency in Table \ref{tab:allow_stand_data}.	
	\item Strike: The option strike price.\\
	Allowable values:  Any positive real number.	
	\item Quantity: The number of units of the underlying commodity covered by the transaction. \\
	Allowable values:  Any positive real number.
\end{itemize}

\subsubsection{Commodity Forward}

The \lstinline!CommodityForwardData!  node is the trade data container for the commodity forward trade type.   The structure of an example \lstinline!CommodityForwardData! node for an equity option is shown in 
Listing \ref{lst:comfwd_data}.

\begin{listing}[H]
%\hrule\medskip
\begin{minted}[fontsize=\footnotesize]{xml}
<CommodityForwardData>
  <LongShort>Long</LongShort>
  <Maturity>2018-06-30</Maturity>
  <Name>COMDTY_GOLD_USD</Name>
  <Currency>USD</Currency>
  <Strike>1355</Strike>
  <Quantity>1000</Quantity>
</CommodityForwardData>
\end{minted}
\caption{Commodity Forward data}
\label{lst:comfwd_data}
\end{listing}

The meanings and allowable values of the elements in the \lstinline!CommodityForwardData!  node follow below.

\begin{itemize}
	\item LongShort: Defines whether the underlying commodity will be bought (long) or sold (short). \\
	Allowable values: Long, Short.
	\item Maturity: The maturity date of the forward contract, i.e. the date when the underlying commodity will be bought/sold. \\
	Allowable values: Any date string.
	\item Name: The name of the underlying commodity. \\
	Allowable values:  Any string (provided it is the ID of an equity in the market configuration).
	\item Currency: The  currency of the commodity forward. \\
	Allowable values:  See Currency in Table \ref{tab:allow_stand_data}.	
	\item Strike: The agreed buy/sell price of the commodity forward. \\
	Allowable values:  Any positive real number.	
	\item Quantity: The number of units of the underlying commodity to be bought/sold. \\
	Allowable values:  Any positive real number.
\end{itemize}

