\subsubsection{Equity Auto Delta Hedged Option}
\label{pricing:eq_autodeltahedgedoption}

An Equity Auto Delta Hedged Option is a structured product consisting of $N$
batches of European vanilla equity options, each with an embedded discrete
delta-hedging strategy.  The equity amount at expiry for each batch $i$ is

$$
\text{EqAmount} = \sum_{i=1}^{N}
  \bigl[\text{DeltaHedge}_{\text{Final}}^{i}
       + \text{Premium}^{i}
       - \text{Option}_{\text{Final}}^{i}\bigr]
  \times N^{i}
$$

\paragraph{Delta-hedge accumulation.}
The delta-hedge P\&L for batch $i$ is built up discretely on each business day
from the observation start date to expiry:

\begin{align*}
\text{DeltaHedge}_{t} &= \text{DeltaHedge}_{t-1}
  + \delta_{t-1}\,\bigl(F_{t,T} - F_{t-1,T}\bigr), \\
\text{DeltaHedge}_{\text{Start}} &= 0,
\end{align*}

where $F_{t,T}$ is the contractual forward defined as
$$
F_{t,T} = S_t \cdot e^{r\,\tau(t,T)}
$$
with $r$ the forward rate specified in the trade XML and
$\tau(t,T) = \text{Act}(t,T)/365$ measured on an Actual/365 (Fixed) basis.

The delta on each observation date is the Black--Scholes delta at the
hedging volatility $\sigma_h$:
$$
\delta_t = \Phi\!\bigl(\omega\, d_1\bigr),
\qquad
d_1 = \frac{\ln(F_{t,T}/K) + \tfrac{1}{2}\sigma_h^2\,\tau(t,T)}
           {\sigma_h\sqrt{\tau(t,T)}}
$$
where $\omega = +1$ for a call and $\omega = -1$ for a put, and $\Phi$ is
the standard normal cumulative distribution function.

\paragraph{Pricing decomposition.}
The present value is split into four components for each batch:

\begin{enumerate}
\item \textbf{Realized past hedge P\&L} (observation start to valuation date):
  Computed from historical equity fixings and the discrete delta-hedge
  accumulation formula above.  This is a known cash amount, discounted from
  expiry.

\item \textbf{Future hedge P\&L} (valuation date to expiry):  Modelled as a
  Black--Scholes option value at the hedging volatility $\sigma_h$, using the
  contractual forward dynamics (flat rate curve at $r$, zero dividend curve):
  $$
  C_{\text{hedge}}^{i} = \text{BS}\bigl(S_0,\, K^i,\, \sigma_h,\, r,\, T\bigr)
  $$
  This represents the expected terminal value of the delta-hedging strategy
  from today to expiry.

\item \textbf{Option payoff}:  The expected option payoff valued at market
  volatility and market equity forward curves:
  $$
  C_{\text{market}}^{i} = \text{BS}\bigl(S(0,T),\, K^i,\, \sigma_{\text{mkt}},\, T\bigr)
  $$
  using the standard Black--Scholes model with the market dividend and
  forecasting curves, discounted via the market discount curve.

\item \textbf{Premium}:  The per-unit option premium, discounted from expiry
  to today.
\end{enumerate}

The total present value is then:
$$
\text{PV} = \sum_{i} N^{i} \Bigl[
  \text{realizedPnL}^{i} \cdot P(T)
  + C_{\text{hedge}}^{i}
  + \text{Premium}^{i} \cdot P(T)
  - C_{\text{market}}^{i}
\Bigr]
$$

where $P(T)$ is the discount factor for expiry~$T$.

\medskip
The market-vol option and the hedge-vol option are both priced analytically
using the Black--Scholes formula (Analytic European Engine).  The realized
hedge P\&L and premiums are modelled as deterministic cash flows at expiry.
