\subsubsection{Equity Swap}
\label{pricing::eq_swap}

An Equity Leg is priced by discounting cashflows based on the 
equity forwarding curve:
$$
\NPV_{EqLeg} = \sum_{i=1}^n N(t_{i-1})\cdot \left(\frac{(s(t_i) + \delta(t_i)) \text{FX}_i - s(t_{i-1})\cdot \text{FX}_{i-1}
  }{s(t_{i-1}) \cdot \text{FX}_{i-1}}\right) \cdot P(t_{p,i})
$$
where:
\begin{itemize}
\item $t_0, \ldots, t_n$ the times defining the equity fixing schedule
\item $t_{p,1}, \ldots, t_{p,n}$ the times defining the coupon payment schedule
\item $N(t_i)$: the notional at time $t_i$. If the notional is non-resettable this is given as a fixed number in the
  terms of the swap. If the notional is resettable, we have
  $$N(t_i) = \frac{N(t_0)}{s(t_0) \text{FX}_0} s(t_i) \text{FX}_i = q s(t_i) \text{FX}_i$$
  with a quantity $q := N(t_0) / [ s(t_0) \text{FX}_0 ]$ that is fixed for all coupons.
\item $s(t_i)$: the equity forward price at time $t_i$
\item $\delta(t_i)$: the dividend between time $t_{i-1}$ and $t_i$ for Total Return Swap; $0$ for Price Return Swap 
\item $P(t_{p,i})$: the discount factor for time $t_{p,i}$
\item $\text{FX}_i$: the fx rate converting the equity ccy to the equity leg ccy (if FX conversion is applicable, otherwise set
  this to $1$ in the above formula)
\end{itemize}

\smallskip

\underline{Limitation of the approach}

The model assumes \textbf{continuous and deterministic dividends}, while in reality they are discrete and paid on specific dates.
Because the model cannot capture ex dividend or payment dates, PV and P\&L explanations are generally inaccurate.
As a result, the model has limited suitability for large trading books,
where accurate PV and P\&L explain are required for desk and financial control purposes.

\smallskip

The approach ignores \textbf{gap and wrong way risk}, please compare the corresponding section within \ref{pricing:limitation_trs_wrong_way_risk} of the generic TRS model.

Finally, payments can always be settled, i.e. capital control events are not modelled. This is especially relevant for emerging market TRS.