\subsubsection{Cross Currency Swap}
\label{pricing:ir_ccs}

Cross Currency (XCCY) Swaps are priced using a multi-currency framework of discount 
curves by cash flow currency and forwarding curves per index, and generally have 
notional exchanges at the beginning and the end of the swap set to reflect the 
prevailing FX spot rate on trade date.  However, XCCY Swaps may also be rebalancing, 
having ``FX resets'' (i.e. notional adjustments at each fixing date to compensate the 
FX rate move since last fixing).  This feature has an impact on discount curve 
building (Lichters, Stamm, \& Gallagher, 2015) Ch 4.3 (see Section 7.5 for more 
details on curve building).

\medskip
If a Cross Currency Swap contains capped/floored/collared payments, the pricing 
approach described in the relevant cap/floor instrument methodology is applied 
to the cap/floor components.

\medskip
The present value  of a non-rebalancing XCCY Swap (both legs floating, constant 
notional) receiving currency A and paying currency B can be expressed as follows:
\begin{align*}
\intertext{Base currency NPV}
\NPV &= X_A\cdot \NPV_A - X_B\cdot \NPV_B \\
\intertext{with leg A NPV in currency A}
\NPV_{A} &= -N^{A} \,P^{A}(t_0) 
+ N^{A} \,\sum_{i=1}^{n_A} (f^A_i+s^A_i) \,\delta^A_i\,P^A(t_i^A) 
+ N^{A} \,P^A(t_n^{A}) \\
\intertext{and leg B NPV in currency B}
\NPV_B &= - N^B\, P^B(t_0) + N^B \, \sum_{i=1}^{n_B} (f^B_i 
+ s^{B}_i)\,\delta^B_i\, P^B(t_i^B) + N^B \,P^B(t_n^B)
\end{align*}
where:
\begin{itemize}
%\item $\NPV_A$: the present value at time 0 of the currency A leg expressed in currency A
%\item $\NPV_B$: the present value at time 0 of the currency B leg expressed in currency B
\item $X_A$: the FX spot rate between currency A and the base currency at valuation time
\item $X_B$: the FX spot rate between currency B and the base currency at valuation time
\item $N^A$: the notional of the currency A leg expressed in currency A
\item $N^B$: the notional of the currency B leg expressed in currency B
%N^B : the notional in currency B
\item $P^A(t_i^A)$:  the discount factor for time i for currency A
\item $P^B(t_i^B)$:  the discount factor for time i for currency B
\item $s^{A,B}_i$: the contractual XCCY basis swap spread on leg A resp. B for period $i$ 
\item $f^A_i$: the forward projected IBOR rate for period $i$ for the currency A leg
\item $f^B_i$: the forward projected IBOR rate for period $i$ for the currency B leg
\end{itemize}

We are assuming here that the date of the initial exchange of notionals has not passed yet.
Once passed, these cash flows - like any past flows - are excluded from valuation. 
And moreover, the forward projected rates for both legs will be fixings for the current 
period, assuming fixings in advance.

\medskip
The Swap shown above, exchanging floating for floating interest, is a Cross Currency 
Basis Swap (CCBS). A XCCY Swap may as well exchange fixed for floating or 
fixed for fixed payments. 

%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - 
\subsubsection*{Rebalancing Cross Currency Swap}

The PV for each leg of a rebalancing XCCY Basis Swap between currency A and currency B, 
where the rebalancing happens on leg B, can be expressed as follows:
\begin{align*}
\NPV &= X_A\cdot \NPV_A - X_B\cdot \NPV_B \\
\NPV_A &= -N^A \,P^A(t_0) + N^A\cdot \sum_{i=1}^{n_A} (f^A_i + s^A_i)\,\delta^A_i \, P^A(t_i^A) + N^A\,P^A(t_n^A) \\
\NPV_B & =-N_0^B \,P^B(t_0)
+\sum_{i=1}^{n_B} \left(N_{i-1}^B (f^B_i +s^B_i)\,\delta^B_i +(N_{i-1}^B-N_i^B)\right) \, P^B(t_i^B) 
 + N_{n_B}^B\,P^B(t_{n_B}^B)
\end{align*}
The rebalancing feature causes intermediate notional cash flows $(N^B_{i-1} - N^B_i)$ 
on leg B. The future leg B notional amounts are computed using FX Forward rates
$$
N^B_i = N^A \cdot \frac{X_A(t_i)}{X_B(t_i)} 
$$
such that the future leg B expected notional converted into leg A currency will correspond to 
the constant leg A notional. This approach assumes zero correlation between the
relevant interest and FX rates. Non-zero correlation would lead to a convexity
adjustment, see e.g. \cite{LSG_2015} section 12.5.
